---
title: "Project 4: Data Collection & Wrangling"
format: html
---

1. Loading R packages
```{r}
library(rvest)
library(dplyr)
library(purrr)
library(tidyverse)
library(httr)
library(lubridate)
library(here)
library(jsonlite)

#OMDB API wrappers
library(imdbapi)
library(ROMDB)
```

2. IF you already have wiki data: [skip to 6]
```{r}
wiki_films <- readRDS("data/wiki_films.RDS")
clean_wiki_films <- readRDS("data/clean_wiki_films.RDS")
```

3. IF NOT: Creating a directory for local data 
```{r}
if (!dir.exists(here("data"))) {
  dir.create(here("data"))
}
```

[TEST] code for webscraping list of movies for the year 2000 from Wikipedia
```{r}
#sample code for 1 year (2000)
html <- read_html(
  "https://en.wikipedia.org/wiki/List_of_American_films_of_2000"
)

results <- html %>%
  html_nodes(".wikitable") %>%
  .[-1] %>% #removes the first table because it is for the top highest grossing for the specific year
  html_table()

#combines the separate tables (months) into one data frame, and adds a column with the relevant year
film_2000 <- bind_rows(results) %>%
  mutate(year = 2000)
```

4. [RUN THIS] Obtain list of American movies from Wikipedia from the years 2000 - 2025 
```{r}
#URLs for wikipedia pages for American films 2000-2025
years <- 2000:2025

urls <- paste0(
  "https://en.wikipedia.org/wiki/List_of_American_films_of_",
  years
)

#Function to get all movies from 2000-2025
extract_wiki_movies <- function(url, year) {
  html <- read_html(url)

  results <- html %>%
    html_nodes(".wikitable") %>%
    .[-1] %>%
    html_table()

  bind_rows(results) %>%
    mutate(year = year)
}

#using purrr to apply the custom function for all urls and years specified
wiki_films <- map2_dfr(urls, years, extract_wiki_movies)


#saving data
saveRDS(wiki_films, file = here("data", "wiki_films.RDS"))
```

5. [RUN THIS] Clean wiki_films dataframe
```{r}
clean_wiki_films <- wiki_films %>%
  filter(!is.na(Title)) %>%
  mutate(
    release = mdy(paste(Opening...1, Opening...2, year))
  ) %>%
  rename("Month" = "Opening...1") %>%
  rename("Date" = "Opening...2") %>%
  select(
    -c(
      "...7",
      ".mw-parser-output .tooltip-dotted{border-bottom:1px dotted;cursor:help}Ref."
    )
  ) %>%
  filter(release < "2025-11-18")


#saving the data frame
saveRDS(clean_wiki_films, file = here("data", "clean_wiki_films.RDS"))

```

6. [RUN THIS] Extracting list of films to get data from the IMDB API 
```{r}
#Extracting the list of films
list_films <- clean_wiki_films %>%
  pull(Title)
```

[TEST FOR 20 MOVIES] Use "IMDBAPI" Wrapper (which actually calls the OMDB API, not the IMDB API)
```{r}
#trial code with a list of 20 films
trial <- list_films[1:20]

test <- map_dfr(
  trial,
  ~ find_by_title(
    .x,
    type = "movie",
    season = NULL,
    episode = NULL,
    year_of_release = NULL,
    plot = "short",
    include_tomatoes = FALSE,
    api_key = omdb_api_key()
  )
)

#de-duplicates entries
test <- test %>%
  distinct(imdbID, .keep_all = TRUE)

#saves data
saveRDS(test, file = here("data", "test.RDS"))
```

7. [RUN THIS] Split list of films into separate lists 
```{r}
#splitting list_films into separate smaller lists to run the API
split_list <- function(x, chunk_size) {
  split(x, ceiling(seq_along(x) / chunk_size))
}

list_sep <- split_list(list_films, 950)

#getting separate lists
imap(list_sep, ~ assign(paste0("list_", .y), .x, envir = .GlobalEnv))

```

Run List 1 
```{r}
data_1 <- map_dfr(
  list_1,
  ~ find_by_title(
    .x,
    type = "movie",
    season = NULL,
    episode = NULL,
    year_of_release = NULL,
    plot = "short",
    include_tomatoes = FALSE,
    api_key = omdb_api_key()
  )
)

#de-duplicates entries
data_1 <- data_1 %>%
  distinct(imdbID, .keep_all = TRUE)

saveRDS(data_1, file = here("data", "data_1.RDS"))
```

Run List 2
```{r}
data_2 <- map_dfr(
  list_2,
  ~ find_by_title(
    .x,
    type = "movie",
    season = NULL,
    episode = NULL,
    year_of_release = NULL,
    plot = "short",
    include_tomatoes = FALSE,
    api_key = omdb_api_key()
  )
)

#de-duplicates entries
data_2 <- data_2 %>%
  distinct(imdbID, .keep_all = TRUE)

saveRDS(data_2, file = here("data", "data_2.RDS"))
```

Run List 3 [DONE]
```{r}
data_3 <- map_dfr(
  list_3,
  ~ find_by_title(
    .x,
    type = "movie",
    season = NULL,
    episode = NULL,
    year_of_release = NULL,
    plot = "short",
    include_tomatoes = FALSE,
    api_key = omdb_api_key()
  )
)

#de-duplicates entries
data_3 <- data_3 %>%
  distinct(imdbID, .keep_all = TRUE)

saveRDS(data_3, file = here("data", "data_3.RDS"))
```

Run List 4 [DONE]
```{r}
data_4 <- map_dfr(
  list_4,
  ~ find_by_title(
    .x,
    type = "movie",
    season = NULL,
    episode = NULL,
    year_of_release = NULL,
    plot = "short",
    include_tomatoes = FALSE,
    api_key = omdb_api_key()
  )
)

#de-duplicates entries
data_4 <- data_4 %>%
  distinct(imdbID, .keep_all = TRUE)

saveRDS(data_4, file = here("data", "data_4.RDS"))
```

Run List 5 [DONE]
```{r}
data_5 <- map_dfr(
  list_5,
  ~ find_by_title(
    .x,
    type = "movie",
    season = NULL,
    episode = NULL,
    year_of_release = NULL,
    plot = "short",
    include_tomatoes = FALSE,
    api_key = omdb_api_key()
  )
)

#de-duplicates entries
data_5 <- data_5 %>%
  distinct(imdbID, .keep_all = TRUE)

saveRDS(data_5, file = here("data", "data_5.RDS"))
```

Run List 6 
```{r}
data_6 <- map_dfr(
  list_6,
  ~ find_by_title(
    .x,
    type = "movie",
    season = NULL,
    episode = NULL,
    year_of_release = NULL,
    plot = "short",
    include_tomatoes = FALSE,
    api_key = omdb_api_key()
  )
)

#de-duplicates entries
data_6 <- data_6 %>%
  distinct(imdbID, .keep_all = TRUE)

saveRDS(data_6, file = here("data", "data_6.RDS"))
```

Run List 7 [DONE]
```{r}
data_7 <- map_dfr(
  list_7,
  ~ find_by_title(
    .x,
    type = "movie",
    season = NULL,
    episode = NULL,
    year_of_release = NULL,
    plot = "short",
    include_tomatoes = FALSE,
    api_key = omdb_api_key()
  )
)

#de-duplicates entries
data_7 <- data_7 %>%
  distinct(imdbID, .keep_all = TRUE)

saveRDS(data_7, file = here("data", "data_7.RDS"))
```

Run List 8 
```{r}
data_8 <- map_dfr(
  list_8,
  ~ find_by_title(
    .x,
    type = "movie",
    season = NULL,
    episode = NULL,
    year_of_release = NULL,
    plot = "short",
    include_tomatoes = FALSE,
    api_key = omdb_api_key()
  )
)

#de-duplicates entries
data_8 <- data_8 %>%
  distinct(imdbID, .keep_all = TRUE)

saveRDS(data_8, file = here("data", "data_8.RDS"))
```

Reading in saved data from IMDB API and binding into one large dataset
```{r}

files <- list.files(
  "data",
  pattern = "^data_[0-9]+\\.RDS$",
  full.names = TRUE
)
full_data <- map_dfr(files, readRDS)

saveRDS(full_data, file = here("data", "full_data.RDS"))
```

Data cleaning 
```{r}

movies_clean <- readRDS("data/movies_clean.RDS")

#movies released before 2000 using movies_clean dataset and Released column
movies_clean %>%
  filter(!is.na(Released)) %>%
  filter(year(Released) < 2000) #check for movies released before 2000
```

Final Data Cleaning and Inflation Adjustment
```{r}
# Load necessary libraries
library(tidyverse)
library(lubridate)
library(plotly)
library(viridis)
library(ggridges)
library(scales)
library(corrplot)
library(DT)
library(priceR)

# Set options to avoid scientific notation
options(scipen = 999)
```

Read in data
```{r}
movies <- readRDS("change to your file path of the movies_clean.rds")
```

Inflation Adjustment Preparation
```{r}
# 3. Pre-download inflation data once
cat("Downloading inflation data once...\n")
# Get unique years from the data
years_needed <- movies %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(!is.na(Year), Year >= 1913, Year <= 2024) %>%
  pull(Year) %>%
  unique() %>%
  sort()
```

Get inflation factors for each year
```{r}
# Create inflation lookup table
inflation_factors <- data.frame(
  Year = years_needed,
  Factor = map_dbl(years_needed, function(y) {
    adjust_for_inflation(1, from_date = y, to_date = 2024, country = "US")
  })
)
```

Original data cleaning
```{r}
# 4. Data cleaning with pre-calculated inflation adjustment
movies_clean <- movies %>%
  # Clean year
  mutate(
    Year = as.numeric(Year),

    # Clean box office data
    BoxOffice_clean = str_remove_all(BoxOffice, "[\\$,]"),
    BoxOffice_clean = str_trim(BoxOffice_clean),
    BoxOffice_num = suppressWarnings(as.numeric(BoxOffice_clean)),

    # Clean runtime
    Runtime_num = as.numeric(str_extract(Runtime, "\\d+")),

    # Clean Metascore
    Metascore_num = as.numeric(Metascore),

    # Add time features
    decade = floor(Released_year / 10) * 10,
    era = case_when(
      Released_year < 2000 ~ "Blockbuster Era",
      Released_year < 2010 ~ "Digital Era",
      TRUE ~ "Streaming Era"
    )
  ) %>%
  # Filter out movies with missing data
  filter(
    !is.na(BoxOffice_num),
    BoxOffice_num > 0,
    !is.na(imdbRating),
    !is.na(Year),
    Year >= 1913
  ) %>%
  # Join with pre-calculated inflation factors
  left_join(inflation_factors, by = "Year") %>%
  mutate(
    # Calculate adjusted box office - round to avoid scientific notation
    BoxOffice_adjusted = round(BoxOffice_num * Factor),

    # Calculate inflation multiplier
    inflation_multiplier = round(Factor, 2),

    # Box office tiers (using adjusted values)
    box_office_tier = case_when(
      BoxOffice_adjusted < 1000000 ~ "< $1M",
      BoxOffice_adjusted < 10000000 ~ "$1M - $10M",
      BoxOffice_adjusted < 50000000 ~ "$10M - $50M",
      BoxOffice_adjusted < 100000000 ~ "$50M - $100M",
      BoxOffice_adjusted < 500000000 ~ "$100M - $500M",
      BoxOffice_adjusted < 1000000000 ~ "$500M - $1B",
      TRUE ~ "> $1B"
    ),

    # Box office tiers (nominal, for comparison)
    box_office_tier_nominal = case_when(
      BoxOffice_num < 1000000 ~ "< $1M",
      BoxOffice_num < 10000000 ~ "$1M - $10M",
      BoxOffice_num < 50000000 ~ "$10M - $50M",
      BoxOffice_num < 100000000 ~ "$50M - $100M",
      BoxOffice_num < 500000000 ~ "$100M - $500M",
      BoxOffice_num < 1000000000 ~ "$500M - $1B",
      TRUE ~ "> $1B"
    ),

    # Rating tiers
    rating_tier = case_when(
      imdbRating < 5 ~ "Poor",
      imdbRating < 6.5 ~ "Average",
      imdbRating < 8 ~ "Good",
      TRUE ~ "Excellent"
    )
  ) %>%
  # Remove the Factor column
  select(-Factor)
```

Additional data cleaning 
```{r}
#6. Extract year from Released column and remove those released before 2000 from Released_year column

movies_clean <- movies_clean %>%
  mutate(
    Released_year = year(ymd(Released))
  ) %>%
  filter(Released_year >= 2000)

#7. Remove original "Year" column to avoid confusion
movies_clean <- movies_clean %>%
  select(-Year)

#8. Convert metascore to numeric
movies_clean <- movies_clean %>%
  mutate(
    Metascore = as.numeric(Metascore),
  ) %>%
  select(-Metascore_num)


#9. Convert rating tier to factor with ordered levels
movies_clean <- movies_clean %>%
  mutate(
    rating_tier = factor(
      rating_tier,
      levels = c("Poor", "Average", "Good", "Excellent"),
      ordered = TRUE
    )
  )

#9. Redo the decades and eras based on Released_year column
movies_clean <- movies_clean %>%
  mutate(
    decade = floor(Released_year / 10) * 10,
    era = case_when(
      Released_year < 2000 ~ "Blockbuster Era",
      Released_year < 2010 ~ "Digital Era",
      TRUE ~ "Streaming Era"
    )
  )

#10. box office tier nominal and adjusted as factors with ordered levels
movies_clean <- movies_clean %>%
  mutate(
    box_office_tier_nominal = factor(
      box_office_tier_nominal,
      levels = c(
        "< $1M",
        "$1M - $10M",
        "$10M - $50M",
        "$50M - $100M",
        "$100M - $500M",
        "$500M - $1B",
        "> $1B"
      ),
      ordered = TRUE
    )
  )

# 10. Rated as factor with ordered levels
movies_clean <- movies_clean %>%
  mutate(
    Rated = factor(
      Rated,
      levels = c(
        "G",
        "PG",
        "PG-13",
        "R",
        "NC-17",
        "Not Rated",
        "Unrated"
      ),
      ordered = TRUE
    )
  )
```

Save the cleaned data 
```{r}
# 11. Save the cleaned data with proper formatting
movies_clean_formatted <- movies_clean %>%
  mutate(
    BoxOffice_num = round(BoxOffice_num),
    BoxOffice_adjusted = round(BoxOffice_adjusted)
  )

saveRDS(movies_clean, "movies_clean.rds")
```


```