---
title: "Movie Investment Time Machine"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: cosmo
    navbar:
      - { title: "About", icon: "fa-info-circle", align: right }
runtime: shiny
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}

library(flexdashboard)
library(shiny)
library(tidyverse)
library(plotly)
library(mgcv)
library(randomForest)
library(scales)
library(viridis)
library(DT)
library(tm)
library(caret)
library(stringdist)
library(e1071)   # SVM model

# Global CSS
tags$style(HTML("
  /* Movie poster styles */
  .movie-poster-container {
    position: relative;
    overflow: hidden;
  }
  
  .movie-poster-container img {
    transition: all 0.3s ease;
  }
  
  .movie-poster-container img:hover {
    transform: scale(1.05);
    filter: brightness(1.1);
  }
  
  /* Add a play button overlay on hover */
  .movie-poster-container::after {
    content: '▶';
    position: absolute;
    top: 50%;
    left: 50%;
    transform: translate(-50%, -50%);
    font-size: 40px;
    color: white;
    opacity: 0;
    transition: opacity 0.3s ease;
    pointer-events: none;
    text-shadow: 0 2px 4px rgba(0,0,0,0.5);
  }
  
  .movie-poster-container:hover::after {
    opacity: 0.8;
  }
"))
# Define custom color palette
time_machine_colors <- list(
  primary = "#1f77b4",
  secondary = "#ff7f0e", 
  accent = "#2ca02c",
  warning = "#d62728",
  info = "#17becf",
  gradient = c("#440154", "#31688e", "#35b779", "#fde725")
)
movies_clean <- read_rds("movies_clean.rds")

```

```{r}
# PART 1: FEATURE ENGINEERING


create_advanced_features <- function(movie_data) {
  # Calculate director statistics
  director_stats <- movie_data %>%
    filter(!is.na(Director), !is.na(BoxOffice_num)) %>%
    group_by(Director) %>%
    summarise(
      director_movies = n(),
      director_avg_revenue = mean(BoxOffice_num, na.rm = TRUE),
      director_avg_rating = mean(imdbRating, na.rm = TRUE),
      director_success_rate = mean(BoxOffice_num > 50000000, na.rm = TRUE),
      .groups = "drop"
    )
  
  # Calculate actor statistics
  actor_stats <- movie_data %>%
    filter(!is.na(Actors), !is.na(BoxOffice_num)) %>%
    mutate(lead_actor = str_split(Actors, ", ", simplify = TRUE)[,1]) %>%
    group_by(lead_actor) %>%
    summarise(
      actor_movies = n(),
      actor_avg_revenue = mean(BoxOffice_num, na.rm = TRUE),
      .groups = "drop"
    )
  
  # Create comprehensive features
  movie_features <- movie_data %>%
    filter(!is.na(BoxOffice_num), !is.na(Released_year)) %>%
    mutate(
      # Time features
      years_from_2000 = Released_year - 2000,
      month = month(Released),
      quarter = quarter(Released),
      is_summer = ifelse(!is.na(month), month %in% c(5, 6, 7), FALSE),
      is_holiday = ifelse(!is.na(month), month %in% c(11, 12), FALSE),
      
      # Genre features
      main_genre = str_split(Genre, ", ", simplify = TRUE)[,1],
      genre_count = str_count(Genre, ",") + 1,
      is_action = grepl("Action", Genre),
      is_comedy = grepl("Comedy", Genre),
      is_drama = grepl("Drama", Genre),
      is_horror = grepl("Horror", Genre),
      is_scifi = grepl("Sci-Fi", Genre),
      is_animation = grepl("Animation", Genre),
      
      # Title features
      title_length = nchar(Title),
      is_sequel = grepl("2|3|4|5|II|III|IV|V|Part|Episode|Chapter", Title),
      has_colon = grepl(":", Title),
      
      # Rating features
      is_r_rated = Rated == "R",
      is_pg13 = Rated == "PG-13",
      is_pg = Rated == "PG",
      
      # Score and popularity
      rating_squared = imdbRating^2,
      log_votes = log(imdbVotes + 1),
      votes_per_year = imdbVotes / pmax(1, 2024 - Released_year),
      
      # Runtime features
      is_long_movie = Runtime_num > 120,
      is_short_movie = Runtime_num < 90,
      runtime_squared = Runtime_num^2,
      
      # Awards features
      has_awards = !is.na(Awards) & Awards != "N/A",
      award_count = ifelse(has_awards, 
                          str_count(Awards, "win|Win|won|Won|nomination|Nomination"), 
                          0),
      
      # Production features
      has_production = !is.na(Production) & Production != "N/A",
      
      # Era features
      era = case_when(
        Released_year <= 2005 ~ "early_2000s",
        Released_year <= 2010 ~ "late_2000s",
        Released_year <= 2015 ~ "early_2010s",
        Released_year <= 2020 ~ "late_2010s",
        TRUE ~ "early_2020s"
      ),
      
      # Extract lead actor
      lead_actor = str_split(Actors, ", ", simplify = TRUE)[,1]
    ) %>%
    # Join statistics
    left_join(director_stats, by = "Director") %>%
    left_join(actor_stats, by = "lead_actor") %>%
    # Fill missing values
    mutate(
      director_movies = replace_na(director_movies, 1),
      director_avg_revenue = replace_na(director_avg_revenue, median(BoxOffice_num, na.rm = TRUE)),
      director_avg_rating = replace_na(director_avg_rating, median(imdbRating, na.rm = TRUE)),
      director_success_rate = replace_na(director_success_rate, 0.5),
      actor_movies = replace_na(actor_movies, 1),
      actor_avg_revenue = replace_na(actor_avg_revenue, median(BoxOffice_num, na.rm = TRUE)),
      month = replace_na(month, 6),
      quarter = replace_na(quarter, 2),
      is_summer = replace_na(is_summer, FALSE),
      is_holiday = replace_na(is_holiday, FALSE)
    )
  
  # Remove infinite values and fill remaining NAs
  movie_features <- movie_features %>%
    mutate_if(is.numeric, ~ifelse(is.infinite(.), NA, .)) %>%
    mutate_if(is.numeric, ~replace_na(., median(., na.rm = TRUE)))
  
  return(movie_features)
}

# PART 2: MODEL BUILDING


build_ensemble_model <- function(movie_data) {
  # Prepare data
  model_data <- create_advanced_features(movie_data) %>%
    select(
      BoxOffice_num, years_from_2000, imdbRating, log_votes, Runtime_num,
      genre_count, is_sequel, is_summer, is_holiday, 
      director_avg_revenue, director_avg_rating, actor_avg_revenue,
      is_action, is_comedy, is_drama, is_horror, is_scifi, is_animation,
      rating_squared, votes_per_year, is_long_movie, is_short_movie,
      is_r_rated, is_pg13, is_pg, has_awards, award_count,
      main_genre, era
    ) %>%
    drop_na()
  
  # Split data
  set.seed(123)
  train_idx <- sample(1:nrow(model_data), 0.8 * nrow(model_data))
  train_data <- model_data[train_idx, ]
  test_data <- model_data[-train_idx, ]
  
  # Model 1: GAM
  gam_model <- gam(log(BoxOffice_num) ~ 
                   s(years_from_2000, k = 5) +
                   s(imdbRating, k = 5) +
                   s(log_votes, k = 5) +
                   s(Runtime_num, k = 5) +
                   genre_count +
                   is_sequel +
                   is_summer +
                   is_holiday,
                 data = train_data)
  
  # Model 2: Random Forest
  rf_features <- train_data %>%
    select_if(is.numeric) %>%
    select(-BoxOffice_num)
  
  rf_features <- rf_features[complete.cases(rf_features), ]
  rf_target <- log(train_data$BoxOffice_num[complete.cases(rf_features)])
  
  rf_model <- randomForest(
    x = rf_features,
    y = rf_target,
    ntree = 100,
    mtry = sqrt(ncol(rf_features))
  )
  
  # Model 3: Linear Model
  lm_model <- lm(log(BoxOffice_num) ~ 
                 years_from_2000 +
                 imdbRating +
                 log_votes +
                 Runtime_num +
                 director_avg_revenue +
                 actor_avg_revenue +
                 is_sequel +
                 genre_count +
                 is_summer +
                 is_holiday,
               data = train_data)
  
  # Model 4: SVM Model
  svm_features <- rf_features
  
  svm_model <- e1071::svm(
    x      = svm_features,
    y      = log(train_data$BoxOffice_num),
    kernel = "radial",
    cost   = 1,
    gamma  = 0.1
  )
  
  
  return(list(
    gam         = gam_model,
    rf          = rf_model,
    lm          = lm_model,
    svm         = svm_model,      
    train_data  = train_data,
    test_data   = test_data,
    rf_features = rf_features,
    svm_features = svm_features
  ))
}

# PART 3: PREDICTION FUNCTIONS

predict_multiple_years <- function(movie_data, selected_movie, year_range = 2000:2025) {

  # Build models once
  models <- build_ensemble_model(movie_data)
  all_features <- create_advanced_features(movie_data)
  
  # Get movie info
  movie_info <- movie_data %>%
    filter(Title == selected_movie) %>%
    dplyr::slice(1)
  
  if (nrow(movie_info) == 0) {
    stop(paste("Movie", selected_movie, "not found"))
  }
  
  original_features <- all_features %>%
    filter(Title == selected_movie) %>%
    dplyr::slice(1)
  
  # Predict for each year
  predictions <- map_df(year_range, function(target_year) {
    # Adjust features to target year
    target_features <- original_features %>%
      mutate(
        Released_year = target_year,
        years_from_2000 = target_year - 2000,
        era = case_when(
          target_year <= 2005 ~ "early_2000s",
          target_year <= 2010 ~ "late_2000s",
          target_year <= 2015 ~ "early_2010s",
          target_year <= 2020 ~ "late_2010s",
          TRUE ~ "early_2020s"
        ),
        votes_per_year = imdbVotes / pmax(1, 2024 - target_year)
      )
    
    pred_gam <- exp(predict(models$gam, newdata = target_features))
    
    rf_features <- target_features %>%
      dplyr::select(names(models$rf_features))
    pred_rf <- exp(predict(models$rf, newdata = rf_features))
    
    pred_lm  <- exp(predict(models$lm,  newdata = target_features))
    pred_svm <- exp(predict(models$svm, newdata = target_features))
    
    
    pred_ensemble <- mean(c(pred_gam, pred_rf, pred_lm, pred_svm))
    
    data.frame(
      Year         = target_year,
      GAM          = pred_gam / 1e6,
      RandomForest = pred_rf  / 1e6,
      Linear       = pred_lm  / 1e6,
      SVM          = pred_svm / 1e6,        
      Ensemble     = pred_ensemble / 1e6,
      Is_Original  = (target_year == movie_info$Released_year)
    )

  })
  
  # Add actual box office
  predictions$Actual <- ifelse(predictions$Is_Original, 
                              movie_info$BoxOffice_num / 1e6, 
                              NA)
  
  return(predictions)
}

# PART 4: VISUALIZATIONS

create_timeline_plot <- function(predictions, movie_title) {
  
  # Prepare Box Office Data
  actual_data <- predictions[!is.na(predictions$Actual), ]
  
  # Create Basic Plot
  p <- plot_ly()
  
  # Add Assemble Prediction Line
  p <- p %>%
    add_trace(
      data = predictions,
      x = ~Year,
      y = ~Ensemble,
      type = "scatter",
      mode = "lines+markers",
      name = "Ensemble Prediction",
      line = list(color = "#1f77b4", width = 4),
      marker = list(size = 10, color = "#1f77b4")
    )
  
  # Add Other Prediction Model
  p <- p %>%
    add_trace(
      data = predictions,
      x = ~Year,
      y = ~GAM,
      type = "scatter",
      mode = "lines",
      name = "GAM",
      line = list(color = "#17becf", dash = "dot", width = 2),
      visible = "legendonly"
    ) %>%
    add_trace(
      data = predictions,
      x = ~Year,
      y = ~RandomForest,
      type = "scatter",
      mode = "lines",
      name = "Random Forest",
      line = list(color = "#2ca02c", dash = "dot", width = 2),
      visible = "legendonly"
    ) %>%
    add_trace(
      data = predictions,
      x = ~Year,
      y = ~Linear,
      type = "scatter",
      mode = "lines",
      name = "Linear",
      line = list(color = "#ff7f0e", dash = "dot", width = 2),
      visible = "legendonly"
    )
  
  # Add Actual Box Office
  if (nrow(actual_data) > 0) {
    p <- p %>%
      add_trace(
        data = actual_data,
        x = ~Year,
        y = ~Actual,
        type = "scatter",
        mode = "markers+text",
        name = "Actual Box Office",
        marker = list(
          size = 25,
          color = "#d62728",
          symbol = "circle",  # 使用圆形
          line = list(color = "white", width = 2)  # 白色边框
        ),
        text = paste0("$", round(actual_data$Actual, 1), "M"),
        textposition = "top center",
        textfont = list(size = 12, color = "#d62728")
      )
  }
  
  # Setting Distribution
  p <- p %>%
    layout(
      title = list(
        text = paste("<b>Time Travel Analysis:</b>", movie_title),
        font = list(size = 16)
      ),
      xaxis = list(
        title = "Year",
        gridcolor = "#e0e0e0"
      ),
      yaxis = list(
        title = "Box Office (Million USD)",
        gridcolor = "#e0e0e0"
      ),
      hovermode = "x unified",
      plot_bgcolor = "#fafafa",
      paper_bgcolor = "white",
      legend = list(
        bgcolor = "rgba(255, 255, 255, 0.8)",
        bordercolor = "#333",
        borderwidth = 1
      )
    )
  
  return(p)
}
compare_movies_time_travel <- function(movie_data, movie_list, year_range = 2000:2025) {
  
  cat("Comparing multiple movies across time...\n\n")
  
  # Get predictions for each movie
  all_predictions <- map_df(movie_list, function(movie) {
    cat("Processing:", movie, "\n")
    tryCatch({
      pred <- predict_multiple_years(movie_data, movie, year_range)
      pred$Movie <- movie
      pred
    }, error = function(e) {
      cat("Error with", movie, ":", e$message, "\n")
      NULL
    })
  })
  
  # Create comparison plot
  p <- plot_ly() %>%
    layout(
      title = list(
        text = "<b>Multi-Movie Time Travel Comparison</b>",
        font = list(size = 16)
      ),
      xaxis = list(
        title = "Year",
        gridcolor = "#e0e0e0"
      ),
      yaxis = list(
        title = "Box Office (Million USD)",
        gridcolor = "#e0e0e0"
      ),
      plot_bgcolor = "#fafafa",
      paper_bgcolor = "white",
      hovermode = "x unified"
    )
  
  # Color palette
  colors <- c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728", "#9467bd", "#8c564b")
  
  for (i in seq_along(movie_list)) {
    movie_pred <- all_predictions %>% filter(Movie == movie_list[i])
    
    if (nrow(movie_pred) > 0) {
      # Add prediction line
      p <- p %>%
        add_trace(
          data = movie_pred,
          x = ~Year,
          y = ~Ensemble,
          type = "scatter",
          mode = "lines+markers",
          name = movie_list[i],
          line = list(
            color = colors[i %% length(colors) + 1], 
            width = 3
          ),
          marker = list(
            size = 8,
            color = colors[i %% length(colors) + 1]
          )
        )
      
      # Add actual box office points with circle markers
      actual_point <- movie_pred %>% filter(!is.na(Actual))
      if (nrow(actual_point) > 0) {
        p <- p %>%
          add_trace(
            data = actual_point,
            x = ~Year,
            y = ~Actual,
            type = "scatter",
            mode = "markers",
            name = paste(movie_list[i], "(Actual)"),
            marker = list(
              size = 18, 
              color = colors[i %% length(colors) + 1],
              symbol = "circle-open", 
              line = list(width = 3)
            ),
            showlegend = FALSE
          )
      }
    }
  }
  
  return(list(plot = p, data = all_predictions))
}


# Best year analysis with visualization
find_best_release_year <- function(movie_data, movie_title, year_range = 2000:2025) {
  
  # Get predictions
  predictions <- predict_multiple_years(movie_data, movie_title, year_range)
  
  # Find best and worst years
  best_year <- predictions %>% 
    arrange(desc(Ensemble)) %>% 
    dplyr::slice(1) 
  
  worst_year <- predictions %>% 
    arrange(Ensemble) %>% 
    dplyr::slice(1) 
  
  original <- predictions %>% 
    filter(Is_Original) %>%
    dplyr::slice(1) 
  
  # Calculate statistics
  box_office_stats <- predictions %>%
    summarise(
      avg_box_office = mean(Ensemble),
      sd_box_office = sd(Ensemble),
      box_office_range = max(Ensemble) - min(Ensemble)
    )
  
  # Group by era
  era_performance <- predictions %>%
    mutate(Era = case_when(
      Year <= 2005 ~ "2000-2005",
      Year <= 2010 ~ "2006-2010",
      Year <= 2015 ~ "2011-2015",
      Year <= 2020 ~ "2016-2020",
      TRUE ~ "2021-2025"
    )) %>%
    group_by(Era) %>%
    summarise(
      Avg_Box_Office = mean(Ensemble),
      Max_Box_Office = max(Ensemble),
      Min_Box_Office = min(Ensemble),
      .groups = "drop"
    ) %>%
    arrange(desc(Avg_Box_Office))
  
  # Create summary report
  report <- list(
    movie = movie_title,
    best_year = best_year$Year,
    best_box_office = round(best_year$Ensemble, 1),
    worst_year = worst_year$Year,
    worst_box_office = round(worst_year$Ensemble, 1),
    original_year = ifelse(nrow(original) > 0, original$Year, NA),
    original_box_office = ifelse(nrow(original) > 0, round(original$Actual, 1), NA),
    predicted_original = ifelse(nrow(original) > 0, round(original$Ensemble, 1), NA),
    box_office_range = round(box_office_stats$box_office_range, 1),
    best_era = era_performance$Era[1],
    predictions = predictions,
    era_performance = era_performance
  )
  
  return(report)
}

# Create comprehensive dashboard
create_time_travel_dashboard <- function(movie_data, movie_title) {
  
  # Get data
  predictions <- predict_multiple_years(movie_data, movie_title)
  report <- find_best_release_year(movie_data, movie_title)
  
  # 1. Main timeline with enhanced styling
  p1 <- create_timeline_plot(predictions, movie_title)
  
  # 2. Era comparison with gradient bars
  p2 <- plot_ly(report$era_performance) %>%
    add_trace(
      x = ~Era,
      y = ~Avg_Box_Office,
      type = "bar",
      marker = list(
        color = ~Avg_Box_Office,
        colorscale = list(c(0, "#440154"), c(0.5, "#31688e"), c(1, "#fde725")),
        line = list(color = "white", width = 2)
      ),
      text = ~paste0("$", round(Avg_Box_Office, 1), "M"),
      textposition = "outside",
      textfont = list(size = 14, color = "#333")
    ) %>%
    layout(
      title = list(
        text = "<b>Average Box Office by Era</b>",
        font = list(size = 18, color = "#333")
      ),
      xaxis = list(
        title = "<b>Era</b>",
        tickfont = list(size = 12)
      ),
      yaxis = list(
        title = "<b>Avg Box Office (Million USD)</b>",
        tickfont = list(size = 12)
      ),
      plot_bgcolor = "#fafafa",
      paper_bgcolor = "white",
      showlegend = FALSE
    )
  
  # 3. Model comparison with violin plot
  model_comparison <- predictions %>%
    select(Year, GAM, RandomForest, Linear, Ensemble) %>%
    pivot_longer(cols = -Year, names_to = "Model", values_to = "Box_Office")
  
  p3 <- plot_ly(model_comparison) %>%
    add_trace(
      x = ~Model,
      y = ~Box_Office,
      split = ~Model,
      type = "violin",
      box = list(visible = TRUE),
      meanline = list(visible = TRUE),
      marker = list(
        color = c("#1f77b4", "#2ca02c", "#ff7f0e", "#d62728")
      )
    ) %>%
    layout(
      title = list(
        text = "<b>Model Predictions Distribution</b>",
        font = list(size = 20, color = "#333")
      ),
      xaxis = list(
        title = "<b>Model</b>",
        tickfont = list(size = 12)
      ),
      yaxis = list(
        title = "<b>Box Office (Million USD)</b>",
        tickfont = list(size = 12)
      ),
      plot_bgcolor = "#fafafa",
      paper_bgcolor = "white",
      showlegend = FALSE
    )
  
  # 4. Year-over-year change heatmap
  yoy_change <- predictions %>%
    mutate(
      YoY_Change = (Ensemble - lag(Ensemble)) / lag(Ensemble) * 100,
      Era = case_when(
        Year <= 2005 ~ "2000-2005",
        Year <= 2010 ~ "2006-2010",
        Year <= 2015 ~ "2011-2015",
        Year <= 2020 ~ "2016-2020",
        TRUE ~ "2021-2025"
      )
    ) %>%
    filter(!is.na(YoY_Change))
  
  p4 <- plot_ly(yoy_change) %>%
    add_trace(
      x = ~Year,
      y = ~YoY_Change,
      type = "bar",
      marker = list(
        color = ~YoY_Change,
        colorscale = list(
          c(0, "#d62728"),
          c(0.5, "#ffffff"),
          c(1, "#2ca02c")
        ),
        cmid = 0,
        line = list(color = "#333", width = 1)
      ),
      text = ~paste0(round(YoY_Change, 1), "%"),
      textposition = "outside"
    ) %>%
    layout(
      title = list(
        text = "<b>Year-over-Year Box Office Change</b>",
        font = list(size = 20, color = "#333")
      ),
      xaxis = list(
        title = "<b>Year</b>",
        tickfont = list(size = 12)
      ),
      yaxis = list(
        title = "<b>Change (%)</b>",
        tickfont = list(size = 12),
        zeroline = TRUE,
        zerolinecolor = "#333",
        zerolinewidth = 2
      ),
      plot_bgcolor = "#fafafa",
      paper_bgcolor = "white",
      showlegend = FALSE
    )
  
  return(list(
    timeline = p1,
    era_comparison = p2,
    model_comparison = p3,
    yoy_change = p4,
    report = report
  ))
}

# PART 5: BATCH ANALYSIS

analyze_best_years_batch <- function(movie_data, movie_list) {
  
  cat("\n🎬 Analyzing best release years for multiple movies...\n\n")
  
  results <- map_df(movie_list, function(movie) {
    tryCatch({
      report <- find_best_release_year(movie_data, movie, 2000:2025)
      
      data.frame(
        Movie = movie,
        Original_Year = report$original_year,
        Best_Year = report$best_year,
        Best_Box_Office = report$best_box_office,
        Original_Box_Office = report$original_box_office,
        Improvement = round((report$best_box_office - report$original_box_office) / 
                          report$original_box_office * 100, 1),
        Best_Era = report$best_era,
        stringsAsFactors = FALSE
      )
    }, error = function(e) {
      cat("❌ Error with", movie, "\n")
      NULL
    })
  })
  
  # Create visualization for batch results
  p <- plot_ly(results) %>%
    add_trace(
      x = ~Movie,
      y = ~Original_Box_Office,
      type = "bar",
      name = "Original Box Office",
      marker = list(color = time_machine_colors$info)
    ) %>%
    add_trace(
      x = ~Movie,
      y = ~Best_Box_Office,
      type = "bar",
      name = "Best Possible Box Office",
      marker = list(color = time_machine_colors$accent)
    ) %>%
    layout(
      title = list(
        text = "<b>Original vs Best Possible Box Office</b>",
        font = list(size = 20, color = "#333")
      ),
      xaxis = list(
        title = "<b>Movie</b>",
        tickfont = list(size = 10),
        tickangle = -45
      ),
      yaxis = list(
        title = "<b>Box Office (Million USD)</b>",
        tickfont = list(size = 12)
      ),
      barmode = "group",
      plot_bgcolor = "#fafafa",
      paper_bgcolor = "white",
      legend = list(
        x = 0.7,
        y = 0.95,
        bgcolor = "rgba(255, 255, 255, 0.8)",
        bordercolor = "#333",
        borderwidth = 1
      )
    )
  
  return(list(results = results, plot = p))
}

# PART 6: UTILITY FUNCTIONS

# Quick summary function
quick_time_travel_summary <- function(movie_data, movie_title) {
  predictions <- predict_multiple_years(movie_data, movie_title, 2000:2025)
  
  best <- predictions[which.max(predictions$Ensemble), ]
  worst <- predictions[which.min(predictions$Ensemble), ]
  original <- predictions[predictions$Is_Original, ]
  
  cat("\n🎬", movie_title, "Time Travel Summary:\n")
  cat("━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━\n")
  cat("📅 Best Year:", best$Year, "→ $", round(best$Ensemble, 1), "M\n")
  cat("📅 Worst Year:", worst$Year, "→ $", round(worst$Ensemble, 1), "M\n")
  if (nrow(original) > 0) {
    cat("📅 Original:", original$Year, "→ $", round(original$Actual, 1), "M (Actual)\n")
    cat("💰 Potential Gain: $", round(best$Ensemble - original$Actual, 1), "M (",
        round((best$Ensemble - original$Actual) / original$Actual * 100, 1), "%)\n")
  }
  cat("━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━━\n")
}

# Export results function
export_time_travel_results <- function(predictions, movie_title, filename = NULL) {
  if (is.null(filename)) {
    filename <- paste0("time_travel_", 
                      gsub(" ", "_", tolower(movie_title)), 
                      "_", Sys.Date(), ".csv")
  }
  
  write_csv(predictions, filename)
  cat("✅ Results exported to:", filename, "\n")
}

# ============================================
# PART 7: USAGE EXAMPLES
# ============================================

# Function to run complete analysis
run_complete_time_travel_analysis <- function(movie_data, movie_title) {
  
  # 1. Get predictions
  cat("📊 Calculating predictions across time...\n")
  predictions <- predict_multiple_years(movie_data, movie_title, 2000:2025)
  
  # 2. Create visualizations
  cat("🎨 Creating visualizations...\n")
  timeline_plot <- create_timeline_plot(predictions, movie_title)
  
  # 3. Find best year
  cat("🔍 Finding optimal release year...\n")
  report <- find_best_release_year(movie_data, movie_title)
  
  # 4. Create dashboard
  cat("📈 Building interactive dashboard...\n")
  dashboard <- create_time_travel_dashboard(movie_data, movie_title)
  
  # 5. Quick summary
  quick_time_travel_summary(movie_data, movie_title)
  
  return(list(
    predictions = predictions,
    timeline_plot = timeline_plot,
    report = report,
    dashboard = dashboard
  ))
}


# INTERACTIVE EXPLORATION FUNCTION

explore_movie_time_travel <- function(movie_data) {
  cat("\n🎬 MOVIE TIME TRAVEL EXPLORER 🎬\n")
  cat("Enter a movie title to explore its box office across time.\n")
  cat("Type 'quit' to exit.\n\n")
  
  while (TRUE) {
    movie_title <- readline(prompt = "Movie title: ")
    
    if (tolower(movie_title) == "quit") {
      cat("👋 Thanks for using Movie Time Travel!\n")
      break
    }
    
    # Check if movie exists
    if (!movie_title %in% movie_data$Title) {
      cat("❌ Movie not found. Try again.\n")
      
      # Suggest similar titles
      similar <- movie_data$Title[grepl(movie_title, movie_data$Title, ignore.case = TRUE)]
      if (length(similar) > 0) {
        cat("💡 Did you mean one of these?\n")
        cat(paste("  •", head(similar, 5)), sep = "\n")
      }
      next
    }
    
    # Run analysis
    tryCatch({
      result <- run_complete_time_travel_analysis(movie_data, movie_title)
      
      # Ask what to display
      cat("\nWhat would you like to see?\n")
      cat("1. Timeline plot\n")
      cat("2. Era comparison\n")
      cat("3. Model comparison\n")
      cat("4. Year-over-year changes\n")
      cat("5. Export results\n")
      cat("6. Next movie\n")
      
      choice <- readline(prompt = "Choice (1-6): ")
      
      switch(choice,
        "1" = print(result$timeline_plot),
        "2" = print(result$dashboard$era_comparison),
        "3" = print(result$dashboard$model_comparison),
        "4" = print(result$dashboard$yoy_change),
        "5" = export_time_travel_results(result$predictions, movie_title),
        "6" = next
      )
      
    }, error = function(e) {
      cat("❌ Error:", e$message, "\n")
    })
  }
}

```

# Main Analysis {data-icon="fa-chart-line"}

## Column {.sidebar data-width="250"}

### 🎬 Movie Selection

```{r main_sidebar}
selectInput("movie", "Select Movie:",
            choices = sort(unique(movies_clean$Title)),
            selected = "The Dark Knight")

sliderInput("year_range", "Year Range:",
            min = 2000, max = 2025,
            value = c(2000, 2025))

actionButton("analyze", "🚀 Run Analysis", 
             class = "btn-primary btn-block")

hr()

# Movie info
renderUI({
  req(input$movie)
  movie_info <- movies_clean %>%
    filter(Title == input$movie) %>%
    slice(1)
  
  HTML(paste0(
    '<div class="info-box">',
    '<p><b>Year:</b> ', movie_info$Released_year, '</p>',
    '<p><b>IMDB:</b> ', movie_info$imdbRating, '/10</p>',
    '<p><b>Revenue:</b> $', round(movie_info$BoxOffice_num/1e6, 1), 'M</p>',
    '</div>'
  ))
})
```

### 📋 Analysis Info

```{r}
renderUI({
  req(input$movie)
  
  movie_info <- movies_clean %>%
    filter(Title == input$movie) %>%
    dplyr::slice(1)
  
  HTML(paste0(
    "<div style='padding: 10px; background-color: #f8f9fa; border-radius: 5px;'>",
    "<p><strong>Year:</strong> ", movie_info$Released_year, "</p>",
    "<p><strong>Director:</strong> ", movie_info$Director, "</p>",
    "<p><strong>Genre:</strong> ", movie_info$Genre, "</p>",
    "<p><strong>IMDB:</strong> ", movie_info$imdbRating, "/10</p>",
    "<p><strong>Actual Box Office:</strong> $", 
    round(movie_info$BoxOffice_num/1e6, 1), "M</p>",
    "</div>"
  ))
})
```

## Column {data-width="650"}

### 📈 Time Travel Prediction

```{r}
# Reactive values to store results
analysis_results <- reactiveValues(
  predictions = NULL,
  report = NULL,
  dashboard = NULL
)

# Main timeline plot
output$timeline_plot <- renderPlotly({
  req(input$analyze)
  
  isolate({
    withProgress(message = 'Calculating predictions...', value = 0, {
      incProgress(0.3)
      
      # Get predictions
      predictions <- predict_multiple_years(
        movies_clean, 
        input$movie, 
        input$year_range[1]:input$year_range[2]
      )
      
      incProgress(0.6)
      
      # Store results
      analysis_results$predictions <- predictions
      
      # Create plot
      plot <- create_timeline_plot(predictions, input$movie)
      
      incProgress(1)
      
      plot
    })
  })
})

plotlyOutput("timeline_plot", height = "100%")
```

### 🎭 Model Comparison

```{r}
output$model_comparison <- renderPlotly({
  req(input$analyze)
  req(analysis_results$predictions)
  
  model_comparison <- analysis_results$predictions %>%
    select(Year, GAM, RandomForest, Linear, Ensemble) %>%
    pivot_longer(cols = -Year, names_to = "Model", values_to = "Box_Office")
  
  plot_ly(model_comparison) %>%
    add_trace(
      x = ~Model,
      y = ~Box_Office,
      split = ~Model,
      type = "violin",
      box = list(visible = TRUE),
      meanline = list(visible = TRUE),
      marker = list(
        color = c("#1f77b4", "#2ca02c", "#ff7f0e", "#d62728")
      )
    ) %>%
    layout(
      title = list(
        text = "<b>Model Predictions Distribution</b>",
        font = list(size = 16)
      ),
      xaxis = list(title = "Model"),
      yaxis = list(title = "Box Office (Million USD)"),
      plot_bgcolor = "#fafafa",
      showlegend = FALSE
    )
})

plotlyOutput("model_comparison", height = "100%")
```

## Column {data-width="350"}

### 🏆 Best Release Year

```{r}
output$best_year_box <- renderValueBox({
  req(input$analyze)
  
  report <- isolate({
    find_best_release_year(
      movies_clean, 
      input$movie, 
      input$year_range[1]:input$year_range[2]
    )
  })
  
  analysis_results$report <- report
  
  valueBox(
    value = paste0(report$best_year),
    caption = paste0("Best Year - $", round(report$best_box_office, 1), "M"),
    icon = "fa-trophy",
    color = "success"
  )
})

valueBoxOutput("best_year_box")
```

### 📊 Potential Improvement

```{r}
output$improvement_box <- renderValueBox({
  req(analysis_results$report)
  
  report <- analysis_results$report
  
  if (!is.na(report$original_box_office)) {
    improvement <- round((report$best_box_office - report$original_box_office) / 
                        report$original_box_office * 100, 1)
    
    color <- if(improvement > 0) "success" else "warning"
    
    valueBox(
      value = paste0(improvement, "%"),
      caption = "Potential Improvement",
      icon = "fa-chart-line",
      color = color
    )
  } else {
    valueBox(
      value = "N/A",
      caption = "No Original Data",
      icon = "fa-question",
      color = "info"
    )
  }
})

valueBoxOutput("improvement_box")
```

### 📅 Era Performance

```{r}
output$era_plot <- renderPlotly({
  req(analysis_results$predictions)
  
  era_data <- analysis_results$predictions %>%
    mutate(Era = case_when(
      Year <= 2005 ~ "2000-2005",
      Year <= 2010 ~ "2006-2010",
      Year <= 2015 ~ "2011-2015",
      Year <= 2020 ~ "2016-2020",
      TRUE ~ "2021-2025"
    )) %>%
    group_by(Era) %>%
    summarise(
      Avg_Box_Office = mean(Ensemble),
      .groups = "drop"
    )
  
  plot_ly(era_data) %>%
    add_trace(
      x = ~Era,
      y = ~Avg_Box_Office,
      type = "bar",
      marker = list(
        color = ~Avg_Box_Office,
        colorscale = list(c(0, "#440154"), c(0.5, "#31688e"), c(1, "#fde725")),
        line = list(color = "white", width = 2)
      ),
      text = ~paste0("$", round(Avg_Box_Office, 1), "M"),
      textposition = "outside"
    ) %>%
    layout(
      title = list(text = "<b>Average by Era</b>", font = list(size = 14)),
      xaxis = list(title = ""),
      yaxis = list(title = "Avg Box Office ($M)"),
      showlegend = FALSE,
      height = 300
    )
})

plotlyOutput("era_plot", height = "300px")
```

### 📊 Prediction Summary

```{r}
output$summary_table <- renderDT({
  req(analysis_results$predictions)
  
  summary_data <- analysis_results$predictions %>%
    select(Year, Ensemble, Is_Original, Actual) %>%
    mutate(
      Predicted = round(Ensemble, 1),
      Actual = round(Actual, 1),
      Status = ifelse(Is_Original, "Original", "Predicted")
    ) %>%
    select(Year, Status, Predicted, Actual)
  
  datatable(
    summary_data,
    options = list(
      pageLength = 10,
      dom = 't',
      scrollY = "200px",
      scrollCollapse = TRUE
    ),
    rownames = FALSE
  ) %>%
    formatStyle(
      'Status',
      backgroundColor = styleEqual('Original', '#d4edda')
    )
})

DTOutput("summary_table", height = "250px")
```

# Comparison {data-icon="fa-film"}

## Column {.sidebar data-width="250"}

### Compare Movies

```{r}
selectInput("base_movie", "Base Movie:",
            choices = sort(unique(movies_clean$Title)),
            selected = "The Dark Knight")

selectInput("compare_movies", "Compare with:",
            choices = sort(unique(movies_clean$Title)),
            multiple = TRUE)

sliderInput("comp_year_range", "Year Range:",
            min = 2000, max = 2025,
            value = c(2000, 2025))

actionButton("compare", "📊 Compare", 
             class = "btn-info btn-block")


```

## Column

### 🎬 Multi-Movie Comparison

```{r}
output$comparison_plot <- renderPlotly({
  req(input$compare)
  req(input$compare_movies)
  
  isolate({
    withProgress(message = 'Comparing movies...', value = 0, {
      
      all_movies <- c(input$movie, input$compare_movies)
      
      comparison <- compare_movies_time_travel(
        movies_clean, 
        all_movies, 
        input$year_range[1]:input$year_range[2]
      )
      
      comparison$plot
    })
  })
})

plotlyOutput("comparison_plot", height = "600px")
```

### 📊 Comparison Summary

```{r}
output$comparison_table <- renderDT({
  req(input$compare)
  req(input$compare_movies)
  
  isolate({
    all_movies <- c(input$movie, input$compare_movies)
    
    batch_results <- analyze_best_years_batch(movies_clean, all_movies)
    
    datatable(
      batch_results$results,
      options = list(
        pageLength = 10,
        scrollY = "300px"
      ),
      rownames = FALSE
    ) %>%
      formatRound(columns = c('Best_Box_Office', 'Original_Box_Office'), digits = 1) %>%
      formatStyle(
        'Improvement',
        color = styleInterval(0, c('red', 'green')),
        fontWeight = 'bold'
      )
  })
})

DTOutput("comparison_table", height = "350px")
```

# What If {data-icon="fa-magic"}

## Column {data-width="350"}

### 🎮 Scenario Controls

```{r}
# Create scrollable controls panel
tags$style(HTML("
  .chart-wrapper {
    height: 100%;
    overflow-y: auto;
    padding-right: 10px;
  }
  
  .chart-wrapper::-webkit-scrollbar {
    width: 6px;
  }
  
  .chart-wrapper::-webkit-scrollbar-track {
    background: #f1f1f1;
    border-radius: 3px;
  }
  
  .chart-wrapper::-webkit-scrollbar-thumb {
    background: #888;
    border-radius: 3px;
  }
  
  /* Compact control styling */
  .form-group {
    margin-bottom: 10px !important;
  }
  
  .control-label {
    margin-bottom: 3px !important;
    font-size: 13px !important;
  }
  
  .shiny-input-container {
    margin-bottom: 10px !important;
  }
  
  /* Fix selectInput spacing */
  .selectize-control {
    margin-bottom: 0 !important;
  }
  
  /* Ensure content flows properly */
  .scenario-controls-container {
    display: flex;
    flex-direction: column;
    height: 100%;
  }
"))

# Main container with proper structure
tags$div(
  class = "scenario-controls-container",
  style = "height: 100%; display: flex; flex-direction: column;",
  
  # Fixed header section
  tags$div(
    style = "flex-shrink: 0; padding: 10px;",
    
    # Movie selection
    selectInput("scenario_movie_select", 
                "🎬 Select Movie:",
                choices = sort(unique(movies_clean$Title)),
                selected = "The Dark Knight"),
    
    # Compact movie info
    uiOutput("movie_info_compact")
  ),
  
  # Scrollable controls section
  tags$div(
    class = "chart-wrapper",
    style = "flex: 1; overflow-y: auto; padding: 0 10px 10px 10px;",
    
    # Parameters section
    tags$div(
      h6("📊 Adjust Parameters", style = "margin: 10px 0; font-weight: bold;"),
      
      # Two-column layout for sliders
      fluidRow(
        column(6,
          sliderInput("scenario_rating_slider", 
                      "⭐ IMDb",
                      min = 5, max = 10, value = 8.5, step = 0.1,
                      width = "100%")
        ),
        column(6,
          sliderInput("scenario_runtime_slider", 
                      "⏱️ Runtime",
                      min = 60, max = 240, value = 120, step = 5,
                      width = "100%", post = "m")
        )
      ),
      # 🔒 Hidden Release Year slider (存在但用户看不到)
tags$div(
  style = "display: none;",
  sliderInput("scenario_year_slider",
              "Release Year (hidden)",
              min = 2000, max = 2025, value = 2008,
              width = "100%")
),
      fluidRow(
        column(6,
          selectInput("scenario_month_select", 
                      "📅 Month",
                      choices = setNames(1:12, month.abb),
                      selected = 6,
                      width = "100%")
        ),
        column(6,
          radioButtons("scenario_rating_radio", 
                       "🎭 MPAA",
                       choices = c("PG", "PG-13", "R"),
                       selected = "PG-13",
                       inline = TRUE)
        )
      ),
      
      # Genres in compact format
      h6("🎭 Genres", style = "margin: 10px 0 5px 0; font-weight: bold;"),
      checkboxGroupInput("scenario_genres_check", 
                         label = NULL,
                         choices = c("Action", "Comedy", "Drama", "Horror", 
                                    "Sci-Fi", "Romance", "Thriller", "Animation"),
                         selected = c("Action", "Drama"),
                         inline = TRUE),
      # ML Model selector
      h6("ML Model", style = "margin: 10px 0 5px 0; font-weight: bold;"),
      selectInput(
        "scenario_model_select",
        label = NULL,
        choices = c("Ensemble", "GAM", "Random Forest", "Linear Regression", "SVM"),
        selected = "Ensemble",
        width = "100%"
      ),
      # Run ML Analysis button
      actionButton("run_scenario_btn", 
                   "🔮 Run ML Analysis", 
                   class = "btn-warning btn-block",
                   style = "width: 100%; margin: 15px 0;")
    )
  )
)

# Function to parse awards text and extract wins
parse_awards <- function(awards_text) {
  if(is.na(awards_text) || awards_text == "N/A") {
    return(list(wins = 0, nominations = 0, has_oscar = FALSE))
  }
  
  # Extract wins
  wins <- 0
  win_match <- regmatches(awards_text, regexpr("\\d+\\s+win", awards_text, ignore.case = TRUE))
  if(length(win_match) > 0) {
    wins <- as.numeric(gsub("\\D", "", win_match[1]))
  }
  
  # Extract nominations
  nominations <- 0
  nom_match <- regmatches(awards_text, regexpr("\\d+\\s+nomination", awards_text, ignore.case = TRUE))
  if(length(nom_match) > 0) {
    nominations <- as.numeric(gsub("\\D", "", nom_match[1]))
  }
  
  # Check for Oscar
  has_oscar <- grepl("Oscar", awards_text, ignore.case = TRUE)
  
  return(list(wins = wins, nominations = nominations, has_oscar = has_oscar))
}

# Compact movie info display
output$movie_info_compact <- renderUI({
  req(input$scenario_movie_select)
  
  movie <- movies_clean %>%
    filter(Title == input$scenario_movie_select) %>%
    head(1)
  
  if(nrow(movie) == 0) return(NULL)
  
  # Parse awards
  awards_info <- parse_awards(movie$Awards)
  
  # Movie info card
  tags$div(
    style = "margin: 0 0 15px 0; background: linear-gradient(135deg, #f5f7fa 0%, #c3cfe2 100%); 
            border-radius: 10px; overflow: hidden; box-shadow: 0 2px 8px rgba(0,0,0,0.1);",
    
    # Top section with poster and main info
    tags$div(
      style = "display: flex; padding: 12px; gap: 12px;",
      
      # Poster with overlay
      tags$div(
        style = "position: relative; flex-shrink: 0;",
        if(!is.na(movie$Poster) && movie$Poster != "N/A") {
          tagList(
            tags$img(src = movie$Poster, 
                     style = "width: 60px; height: 90px; object-fit: cover; 
                             border-radius: 6px; box-shadow: 0 2px 4px rgba(0,0,0,0.2);"),
            # Rating badge
            tags$div(
              style = "position: absolute; top: -5px; right: -5px; background: #fbbf24; 
                      color: #78350f; padding: 2px 6px; border-radius: 12px; 
                      font-size: 11px; font-weight: bold; box-shadow: 0 1px 3px rgba(0,0,0,0.3);",
              paste0("★ ", round(movie$imdbRating, 1))
            )
          )
        } else {
          tags$div(
            style = "width: 60px; height: 90px; background: linear-gradient(135deg, #667eea 0%, #764ba2 100%); 
                    border-radius: 6px; display: flex; align-items: center; 
                    justify-content: center; color: white; font-size: 24px;
                    box-shadow: 0 2px 4px rgba(0,0,0,0.2);",
            "🎬"
          )
        },
      ),
      
      # Movie details
      tags$div(
        style = "flex: 1; min-width: 0;",
        
        # Title and year
        tags$div(
          style = "margin-bottom: 6px;",
          tags$div(
            style = "font-size: 14px; font-weight: 600; color: #1a202c; 
                    line-height: 1.2; margin-bottom: 2px;",
            movie$Title
          ),
          tags$div(
            style = "font-size: 11px; color: #4a5568;",
            paste0(movie$Released_year, " • ", movie$Rated, " • ", movie$Runtime_num, " min")
          )
        ),
        
        # Genre tags
        tags$div(
          style = "display: flex; flex-wrap: wrap; gap: 4px; margin-bottom: 6px;",
          lapply(unlist(strsplit(movie$Genre, ", "))[1:min(3, length(unlist(strsplit(movie$Genre, ", "))))], function(genre) {
            tags$span(
              style = "background: rgba(99, 102, 241, 0.1); color: #5b21b6; 
                      padding: 2px 6px; border-radius: 4px; font-size: 10px;",
              genre
            )
          })
        ),
        
        # Box office and awards
        tags$div(
          style = "display: flex; align-items: center; gap: 12px;",
          tags$div(
            style = "font-size: 12px; color: #059669; font-weight: 500;",
            paste0("💰 $", formatC(movie$BoxOffice_num/1e6, format = "f", digits = 1, big.mark = ","), "M")
          ),
          # Awards badge if any
          if(awards_info$wins > 0 || awards_info$has_oscar) {
            tags$div(
              style = "font-size: 11px; background: #fef3c7; color: #92400e; 
                      padding: 2px 6px; border-radius: 4px;",
              if(awards_info$has_oscar) {
                paste0("🏆 Oscar Winner")
              } else {
                paste0("🏆 ", awards_info$wins, " wins")
              }
            )
          }
        )
      )
    ),
    
    # Bottom section with additional metrics
    tags$div(
      style = "background: rgba(255,255,255,0.5); padding: 8px 12px; 
              border-top: 1px solid rgba(0,0,0,0.05);",
      tags$div(
        style = "display: grid; grid-template-columns: repeat(3, 1fr); gap: 8px; text-align: center;",
        
        # Metascore
        tags$div(
          tags$div(style = "font-size: 16px; font-weight: bold; color: #7c3aed;",
                   ifelse(!is.na(movie$Metascore), movie$Metascore, "—")),
          tags$div(style = "font-size: 9px; color: #6b7280; margin-top: 2px;", "Metascore")
        ),
        
        # IMDb Votes
        tags$div(
          tags$div(style = "font-size: 16px; font-weight: bold; color: #2563eb;",
                   ifelse(!is.na(movie$imdbVotes), 
                          paste0(round(movie$imdbVotes/1000), "K"), "—")),
          tags$div(style = "font-size: 9px; color: #6b7280; margin-top: 2px;", "Votes")
        ),
        
        # Awards count
        tags$div(
          tags$div(
            style = paste0("font-size: 16px; font-weight: bold; color: ",
                          ifelse(awards_info$has_oscar, "#f59e0b", 
                                ifelse(awards_info$wins > 0, "#dc2626", "#6b7280")), ";"),
            if(awards_info$has_oscar) {
              "🏆"
            } else if(awards_info$wins > 0) {
              awards_info$wins
            } else if(awards_info$nominations > 0) {
              paste0(awards_info$nominations, "n")
            } else {
              "—"
            }
          ),
          tags$div(style = "font-size: 9px; color: #6b7280; margin-top: 2px;", 
                   if(awards_info$wins > 0) "Wins" else "Awards")
        )
      )
    )
  )
})
```

## Column {data-width="350"}

### ML Model What-If Analysis

```{r}
# Calculate ML predictions based on user's scenario inputs
scenario_ml_results <- eventReactive(input$run_scenario_btn, {
  
  # Get original movie data
  original_movie <- movies_clean %>%
    filter(Title == input$scenario_movie_select) %>%
    head(1)
  
  if(nrow(original_movie) == 0) return(NULL)
  
  withProgress(message = 'Running ML models...', value = 0, {
    
    # Build ensemble ML models
    incProgress(0.3, detail = "Building models...")
    models <- build_ensemble_model(movies_clean)
    all_features <- create_advanced_features(movies_clean)
    
    # Get original movie features
    original_features <- all_features %>%
      filter(Title == input$scenario_movie_select) %>%
      head(1)
    
    if(nrow(original_features) == 0) return(NULL)
    
    # Create modified features based on user inputs
    incProgress(0.6, detail = "Creating scenarios...")
    modified_features <- original_features
    
    # Update features with user's scenario values
    modified_features$imdbRating <- input$scenario_rating_slider
    modified_features$Runtime_num <- input$scenario_runtime_slider
    modified_features$Released_year <- original_movie$Released_year
    modified_features$years_from_2000 <- original_movie$Released_year - 2000
    modified_features$month <- as.numeric(input$scenario_month_select)
    modified_features$is_summer <- as.numeric(input$scenario_month_select) %in% c(5, 6, 7)
    modified_features$is_holiday <- as.numeric(input$scenario_month_select) %in% c(11, 12)
    
    # Update MPAA rating features
    modified_features$is_r_rated <- input$scenario_rating_radio == "R"
    modified_features$is_pg13 <- input$scenario_rating_radio == "PG-13"
    modified_features$is_pg <- input$scenario_rating_radio == "PG"
    
    # Update genre features
    modified_features$is_action <- "Action" %in% input$scenario_genres_check
    modified_features$is_comedy <- "Comedy" %in% input$scenario_genres_check
    modified_features$is_drama <- "Drama" %in% input$scenario_genres_check
    modified_features$is_horror <- "Horror" %in% input$scenario_genres_check
    modified_features$is_scifi <- "Sci-Fi" %in% input$scenario_genres_check
    modified_features$is_animation <- "Animation" %in% input$scenario_genres_check
    modified_features$genre_count <- length(input$scenario_genres_check)
    
    # Update derived features
    modified_features$rating_squared <- input$scenario_rating_slider^2
    modified_features$runtime_squared <- input$scenario_runtime_slider^2
    modified_features$is_long_movie <- input$scenario_runtime_slider > 120
    modified_features$is_short_movie <- input$scenario_runtime_slider < 90
    
    # Make predictions using ensemble models
    incProgress(0.8, detail = "Making predictions...")
    
   
    pred_gam_orig <- exp(predict(models$gam, newdata = original_features))
    
    rf_features_orig <- original_features[, names(models$rf_features), drop = FALSE]
    pred_rf_orig  <- exp(predict(models$rf,  newdata = rf_features_orig))
    
    pred_lm_orig  <- exp(predict(models$lm,  newdata = original_features))
    
   
    pred_gam_mod <- exp(predict(models$gam, newdata = modified_features))
    
    rf_features_mod <- modified_features[, names(models$rf_features), drop = FALSE]
    pred_rf_mod  <- exp(predict(models$rf,  newdata = rf_features_mod))
    
    pred_lm_mod  <- exp(predict(models$lm,  newdata = modified_features))
    
    
    
    model_choice <- input$scenario_model_select
    
    if (model_choice == "GAM") {
      
      pred_orig_use <- pred_gam_orig
      pred_mod_use  <- pred_gam_mod
      
    } else if (model_choice == "Random Forest") {
      
      pred_orig_use <- pred_rf_orig
      pred_mod_use  <- pred_rf_mod
      
    } else if (model_choice == "Linear Regression") {
      
      pred_orig_use <- pred_lm_orig
      pred_mod_use  <- pred_lm_mod
      
    } else if (model_choice == "SVM") {
     
      
      svm_vars <- c(
        "years_from_2000", "imdbRating", "log_votes", "Runtime_num",
        "director_avg_revenue", "actor_avg_revenue",
        "is_sequel", "genre_count", "is_summer", "is_holiday"
      )
      
      
      svm_train_x <- all_features[, svm_vars]
      svm_train_y <- log(all_features$BoxOffice_num)
      
      svm_model <- e1071::svm(
        x      = svm_train_x,
        y      = svm_train_y,
        kernel = "radial",
        cost   = 1,
        gamma  = 0.1
      )
      
     
      svm_orig_x <- original_features[, svm_vars, drop = FALSE]
      svm_mod_x  <- modified_features[, svm_vars, drop = FALSE]
      
      pred_orig_use <- exp(predict(svm_model, newdata = svm_orig_x))
      pred_mod_use  <- exp(predict(svm_model, newdata = svm_mod_x))
      
    } else {  
      
      pred_orig_use <- mean(c(pred_gam_orig, pred_rf_orig, pred_lm_orig))
      pred_mod_use  <- mean(c(pred_gam_mod, pred_rf_mod, pred_lm_mod))
    }
    
    incProgress(1, detail = "Done!")

    
    # Return results
    list(
      movie_title        = original_movie$Title,
      selected_model     = model_choice,
      actual_boxoffice   = original_movie$BoxOffice_num / 1e6,
      predicted_original = pred_orig_use / 1e6,
      predicted_modified = pred_mod_use / 1e6,
      change_percent     = (pred_mod_use - pred_orig_use) / pred_orig_use * 100
    )
  })
})

# Create interactive gauge visualization for ML predictions
renderPlotly({
  req(scenario_ml_results())
  results <- scenario_ml_results()
  print(results)
  str(results)

  # Create gauge chart
  fig <- plot_ly(
    type = "indicator",
    mode = "gauge+number+delta",
    value = results$predicted_modified,
    number = list(suffix = "M", font = list(size = 40)),
    delta = list(
      reference = results$predicted_original,
      increasing = list(color = "#2ca02c"),
      decreasing = list(color = "#d62728"),
      suffix = "M",
      font = list(size = 20)
    ),
    gauge = list(
      axis = list(
        range = list(0, max(results$actual_boxoffice, results$predicted_original, 
                           results$predicted_modified) * 1.5),
        tickwidth = 1,
        tickcolor = "darkblue"
      ),
      bar = list(color = "#ffc107"),
      bgcolor = "white",
      borderwidth = 2,
      bordercolor = "gray",
      steps = list(
        list(range = c(0, results$actual_boxoffice), 
             color = "rgba(31, 119, 180, 0.3)"),
        list(range = c(results$actual_boxoffice, results$predicted_original), 
             color = "rgba(44, 160, 44, 0.3)")
      ),
      threshold = list(
        line = list(color = "red", width = 4),
        thickness = 0.75,
        value = results$actual_boxoffice
      )
    ),
    domain = list(x = c(0, 1), y = c(0.3, 1))
  )
  # Add annotations showing actual and original prediction
  fig <- fig %>%
    add_annotations(
      x = 0.5,
      y = 0.2,
      text = paste0(
        "<b>", results$movie_title, "</b><br>",
        "Actual: $", round(results$actual_boxoffice, 1), "M | ",
        "Original Prediction: $", round(results$predicted_original, 1), "M"
      ),
      showarrow = FALSE,
      font = list(size = 14)
    )
  
  # Configure layout
  fig %>%
    layout(
      title = list(
        text = "ML Box Office Prediction with Your Changes",
        font = list(size = 18)
      ),
      height = 350,
      margin = list(t = 80, b = 80)
    )
})
```

### Change Summary

```{r}
# Display summary of changes and their impact on box office prediction
renderUI({
  req(scenario_ml_results())
  results <- scenario_ml_results()
  
  # Get original movie data for comparison
  original_movie <- movies_clean %>%
    filter(Title == input$scenario_movie_select) %>%
    head(1)
  
  # Calculate parameter changes
  rating_change <- input$scenario_rating_slider - original_movie$imdbRating
  year_change <- input$scenario_year_slider - original_movie$Released_year
  runtime_change <- input$scenario_runtime_slider - original_movie$Runtime_num
  
  # Create HTML summary display
  HTML(paste0(
    '<div style="padding: 20px;">',
    
    # Box office comparison cards
    '<div style="display: flex; gap: 15px; margin-bottom: 20px;">',
    
    # Actual box office card
    '<div style="flex: 1; background: linear-gradient(135deg, #667eea 0%, #764ba2 100%); ',
    'color: white; padding: 15px; border-radius: 8px; text-align: center; ',
    'box-shadow: 0 4px 6px rgba(0,0,0,0.1);">',
    '<h6 style="margin: 0; opacity: 0.9; font-size: 14px;">Actual Box Office</h6>',
    '<h3 style="margin: 8px 0; font-size: 28px;">$', round(results$actual_boxoffice, 1), 'M</h3>',
    '</div>',
    
    # ML original prediction card
    '<div style="flex: 1; background: linear-gradient(135deg, #f093fb 0%, #f5576c 100%); ',
    'color: white; padding: 15px; border-radius: 8px; text-align: center; ',
    'box-shadow: 0 4px 6px rgba(0,0,0,0.1);">',
    '<h6 style="margin: 0; opacity: 0.9; font-size: 14px;">ML Original</h6>',
    '<h3 style="margin: 8px 0; font-size: 28px;">$', round(results$predicted_original, 1), 'M</h3>',
    '</div>',
    
    # User's scenario prediction card
    '<div style="flex: 1; background: linear-gradient(135deg, #fa709a 0%, #fee140 100%); ',
    'color: white; padding: 15px; border-radius: 8px; text-align: center; ',
    'box-shadow: 0 4px 6px rgba(0,0,0,0.1);">',
    '<h6 style="margin: 0; opacity: 0.9; font-size: 14px;">Your Scenario</h6>',
    '<h3 style="margin: 8px 0; font-size: 28px;">$', round(results$predicted_modified, 1), 'M</h3>',
    '<p style="margin: 0; font-size: 16px; font-weight: bold;">',
    ifelse(results$change_percent > 0, '↑', '↓'),
    ' ', abs(round(results$change_percent, 1)), '%',
    '</p>',
    '</div>',
    
    '</div>',
    
    # Key changes section
    '<h5 style="margin-bottom: 15px;">🔄 Key Changes Made</h5>',
    '<div style="display: flex; gap: 10px; flex-wrap: wrap;">',
    
    # IMDb rating change box
    '<div style="flex: 1; min-width: 120px; background: #f8f9fa; padding: 10px; ',
    'border-radius: 5px; text-align: center;">',
    '<small style="color: #6c757d;">IMDb Rating</small><br>',
    '<strong>', round(original_movie$imdbRating, 1), ' → ', input$scenario_rating_slider, '</strong><br>',
    '<span style="color: ', ifelse(rating_change > 0, '#2ca02c', '#d62728'), '; font-weight: bold;">',
    ifelse(rating_change > 0, '+', ''), round(rating_change, 1),
    '</span>',
    '</div>',
    
    # Release year change box
    '<div style="flex: 1; min-width: 120px; background: #f8f9fa; padding: 10px; ',
    'border-radius: 5px; text-align: center;">',
    '<small style="color: #6c757d;">Release Year</small><br>',
    '<strong>', original_movie$Released_year, ' → ', input$scenario_year_slider, '</strong><br>',
    '<span style="color: ', ifelse(year_change > 0, '#2ca02c', '#d62728'), '; font-weight: bold;">',
    ifelse(year_change > 0, '+', ''), year_change, ' years',
    '</span>',
    '</div>',
    
    # Runtime change box
    '<div style="flex: 1; min-width: 120px; background: #f8f9fa; padding: 10px; ',
    'border-radius: 5px; text-align: center;">',
    '<small style="color: #6c757d;">Runtime</small><br>',
    '<strong>', original_movie$Runtime_num, ' → ', input$scenario_runtime_slider, '</strong><br>',
    '<span style="color: ', ifelse(runtime_change > 0, '#2ca02c', '#d62728'), '; font-weight: bold;">',
    ifelse(runtime_change > 0, '+', ''), runtime_change, ' min',
    '</span>',
    '</div>',
    
    # Genre count change box
    '<div style="flex: 1; min-width: 120px; background: #f8f9fa; padding: 10px; ',
    'border-radius: 5px; text-align: center;">',
    '<small style="color: #6c757d;">Genres</small><br>',
    '<strong>', length(strsplit(original_movie$Genre, ", ")[[1]]), ' → ', 
    length(input$scenario_genres_check), '</strong><br>',
    '<span style="color: #1f77b4; font-weight: bold;">',
    length(input$scenario_genres_check), ' selected',
    '</span>',
    '</div>',
    
    '</div>',
    '</div>'
  ))
})


```

## Column {data-width="350"}

### 🧪 AI Recipe Generator {style="height:100%; overflow-y:auto;"}

```{r}
# HELPER FUNCTIONS

# Null coalescing operator
`%||%` <- function(x, y) {
  if (is.null(x) || length(x) == 0 || all(is.na(x))) y else x
}

# Safe sampling function with NA handling
safe_sample <- function(x, size = 1, prob = NULL) {
  # Remove NA values
  x <- x[!is.na(x)]
  
  if(length(x) == 0) return(NULL)
  if(length(x) == 1) return(x)
  
  size <- min(size, length(x))
  
  if(!is.null(prob) && length(prob) == length(x)) {
    # Remove NA probabilities
    valid_idx <- !is.na(prob)
    x <- x[valid_idx]
    prob <- prob[valid_idx]
    
    if(length(x) == 0) return(NULL)
    if(sum(prob) > 0) {
      prob <- prob / sum(prob)
      return(sample(x, size, prob = prob))
    }
  }
  
  return(sample(x, size))
}


# Clean generated text
clean_generated_text <- function(text) {
  if(is.null(text) || is.na(text)) return("")
  
  text <- gsub("\\s+", " ", text)
  text <- gsub("\\s+([.,!?])", "\\1", text)
  text <- gsub("([.,!?])([A-Z])", "\\1 \\2", text)
  text <- gsub("\\.+", ".", text)
  text <- gsub("^(.)", "\\U\\1", text, perl = TRUE)
  text <- gsub("([.!?]\\s+)([a-z])", "\\1\\U\\2", text, perl = TRUE)
  
  return(trimws(text))
}

# UI INTERFACE

tags$div(
  style = "height: 100%; overflow-y: auto; padding: 15px;",
  
  h5("🎯 Investment Parameters", style = "margin-top: 0;"),
  
  sliderInput("target_boxoffice", 
              "💰 Target Box Office Revenue:",
              min = 50, max = 1000, value = 300, step = 25,
              width = "100%",
              post = " Million USD"),
  
  radioButtons("optimization_type", 
               "📊 Optimization Strategy:",
               choices = list(
                 "Maximize Revenue 💰" = "boxoffice",
                 "Maximize Rating ⭐" = "rating",
                 "Balanced Approach ⚖️" = "balanced"
               ),
               selected = "balanced",
               inline = TRUE),
  
  hr(),
  
  h5("🤖 AI Model Configuration", style = "margin-top: 15px;"),
  
  radioButtons("ai_model_type", 
               "Select AI Model:",
               choices = list(
                 "Transformer-based (GPT-style)" = "transformer",
                 "LSTM Sequential" = "lstm",
                 "Ensemble Learning" = "ensemble",
                 "Markov Chain Monte Carlo" = "mcmc"
               ),
               selected = "transformer"),
  
  tags$div(
  style = "margin-bottom: 20px;",
  
  tags$label("🌡️ Generation Temperature:", 
             style = "display: block; margin-bottom: 15px; font-weight: 500;"),
  
  tags$div(
    style = "position: relative; padding: 20px 0 10px 0;",
    tags$div(
      style = "position: absolute; top: 0; left: 12px; right: 12px; height: 8px;
              background: linear-gradient(to right, #3b82f6 0%, #ef4444 100%);
              border-radius: 4px; opacity: 0.2;"
    ),
    tags$div(
      style = "display: flex; justify-content: space-between; margin-bottom: 5px; padding: 0 12px;",
      tags$span("🧊 Conservative", style = "color: #3b82f6; font-size: 13px; font-weight: 500;"),
      tags$span("🔥 Creative", style = "color: #ef4444; font-size: 13px; font-weight: 500;")
    ),
    sliderInput("generation_temperature", 
                label = NULL,
                min = 0.1, max = 2.0, value = 0.8, step = 0.1,
                width = "100%")
  )
),
  
  selectInput("sampling_method", 
              "Sampling Strategy:",
              choices = list(
                "Top-K Sampling" = "topk",
                "Nucleus (Top-P)" = "nucleus",
                "Beam Search" = "beam",
                "Greedy" = "greedy"
              ),
              selected = "nucleus"),
  
  hr(),
  
  h5("🎬 Content Parameters", style = "margin-top: 15px;"),
  
  selectInput("primary_genre", 
              "Primary Genre:",
              choices = list(
                "Action/Adventure" = "action",
                "Drama" = "drama",
                "Comedy" = "comedy",
                "Thriller" = "thriller",
                "Sci-Fi" = "scifi",
                "Horror" = "horror"
              ),
              selected = "action"),
  
  sliderInput("originality_score", 
              "💡 Originality Level:",
              min = 1, max = 10, value = 7,
              pre = "Familiar ", post = " Innovative"),
  
  actionButton("generate_ai_movie", 
               "🚀 Generate with AI", 
               class = "btn-primary btn-block",
               style = "width: 100%; margin: 20px 0; font-size: 16px; padding: 12px;"),
  
  uiOutput("ai_movie_result")
)

# MAIN GENERATION LOGIC

observeEvent(input$generate_ai_movie, {
  
  withProgress(message = 'Initializing AI models...', value = 0, {
    
    tryCatch({
      
      # Step 1: Validate inputs
      incProgress(0.1, detail = "Validating inputs...")
      
      genre_input <- input$primary_genre %||% "action"
      target_boxoffice <- as.numeric(input$target_boxoffice) * 1e6
      optimization_type <- input$optimization_type
      ai_model_type <- input$ai_model_type
      temperature <- as.numeric(input$generation_temperature)
      sampling_method <- input$sampling_method
      originality <- as.numeric(input$originality_score)
      
      # Step 2: Prepare data
      incProgress(0.2, detail = "Preparing movie data...")
      
      genre_filter <- switch(genre_input,
        "action" = "Action",
        "drama" = "Drama",
        "comedy" = "Comedy",
        "thriller" = "Thriller",
        "scifi" = "Sci-Fi",
        "horror" = "Horror",
        "Action"
      )
      
      relevant_movies <- movies_clean %>%
        filter(
          !is.na(Title),
          !is.na(Plot),
          nchar(Plot) > 50,
          !is.na(BoxOffice_num),
          !is.na(imdbRating)
        ) %>%
        filter(
          grepl(genre_filter, Genre, ignore.case = TRUE) | row_number() <= 100
        ) %>%
        mutate(
          success_score = case_when(
            optimization_type == "boxoffice" ~ scale(BoxOffice_num)[,1],
            optimization_type == "rating" ~ scale(imdbRating)[,1],
            TRUE ~ (scale(BoxOffice_num)[,1] + scale(imdbRating)[,1]) / 2
          )
        ) %>%
        arrange(desc(success_score)) %>%
        head(50)
      
      if(nrow(relevant_movies) < 10) {
        stop("Insufficient data for selected genre")
      }
      
      # Step 3: Initialize AI model
      incProgress(0.3, detail = "Initializing AI model...")
      
      ai_model <- list(
        type = ai_model_type,
        temperature = temperature,
        sampling = sampling_method,
        patterns = extract_patterns_optimized(relevant_movies)
      )
      
      # Step 4: Generate title
      incProgress(0.4, detail = "Generating title...")
      
      generated_title <- generate_title_with_ai(
        movies = relevant_movies,
        model = ai_model,
        originality = originality
      )
      
      # Step 5: Generate plot
      incProgress(0.5, detail = "Creating plot...")
      
      generated_plot <- generate_plot_with_ai(
        movies = relevant_movies,
        model = ai_model,
        genre = genre_filter,
        title = generated_title
      )
      
      # Step 6: Select team
      incProgress(0.6, detail = "Selecting optimal team...")
      
      team <- select_team_with_ml(
        movies = relevant_movies,
        optimization = optimization_type
      )
      
      # Step 7: Determine configuration
      incProgress(0.7, detail = "Optimizing configuration...")
      
      config <- optimize_movie_config(
        movies = relevant_movies,
        target_boxoffice = target_boxoffice,
        optimization = optimization_type
      )
      
      # Step 8: Create movie object (NO BUDGET)
      generated_movie <- list(
        title = generated_title,
        plot = generated_plot,
        director = team$director,
        cast = team$cast,
        genres = config$genres,
        runtime = config$runtime,
        release_month = config$release_month,
        mpaa_rating = config$mpaa_rating,
        ai_model = ai_model_type,
        optimization = optimization_type
      )
      
      # Step 9: Predict performance
      incProgress(0.8, detail = "Predicting performance...")
      
      performance <- predict_performance_ml(
        movie = generated_movie,
        reference_movies = relevant_movies,
        optimization = optimization_type
      )
      
      # Step 10: Display results
      incProgress(0.9, detail = "Preparing visualization...")
      
      output$ai_movie_result <- renderUI({
        create_enhanced_result_ui(
          movie = generated_movie,
          performance = performance,
          model_info = ai_model
        )
      })
      
      incProgress(1, detail = "Complete!")
      showNotification("🎬 AI Movie Generated Successfully!", type = "message")
      
    }, error = function(e) {
      showNotification(
        paste("Generation failed:", e$message),
        type = "error",
        duration = 5
      )
      
      output$ai_movie_result <- renderUI({
        tags$div(
          style = "padding: 20px; background: #fff5f5; border: 1px solid #feb2b2; border-radius: 8px; margin-top: 20px;",
          tags$h5("⚠️ Generation Error", style = "color: #c53030;"),
          tags$p("Unable to generate movie with current settings."),
          tags$small(
            style = "color: #718096;",
            "Error: ", tags$code(e$message)
          ),
          tags$hr(),
          tags$p("Try adjusting your parameters or selecting a different genre.")
        )
      })
    })
  })
})

# PATTERN EXTRACTION

extract_patterns_optimized <- function(movies) {
  patterns <- list()
  
  # Extract titles (remove NAs)
  patterns$titles <- movies$Title[!is.na(movies$Title) & movies$Title != ""]
  
  if(length(patterns$titles) == 0) {
    patterns$titles <- c("The Movie")
  }
  
  # Title word frequency
  title_words <- unlist(strsplit(patterns$titles, "\\s+"))
  title_words <- title_words[!is.na(title_words) & title_words != ""]
  
  if(length(title_words) > 0) {
    patterns$title_freq <- sort(table(title_words), decreasing = TRUE)
  } else {
    patterns$title_freq <- table(c("The", "Movie"))
  }
  
  # Plot patterns
  valid_plots <- movies$Plot[!is.na(movies$Plot) & nchar(movies$Plot) > 50]
  
  if(length(valid_plots) > 0) {
    patterns$openings <- unique(substr(valid_plots, 1, 100))
    patterns$openings <- patterns$openings[!is.na(patterns$openings)]
    patterns$openings <- patterns$openings[1:min(10, length(patterns$openings))]
  } else {
    patterns$openings <- c("In a world where anything is possible")
  }
  
  # Extract conflicts safely
  patterns$conflicts <- tryCatch({
    if(length(valid_plots) > 0) {
      conflicts <- unlist(str_extract_all(valid_plots, "(must|has to|needs to|forced to) [^.]+"))
      conflicts <- conflicts[!is.na(conflicts) & conflicts != ""]
      unique(conflicts)[1:min(10, length(conflicts))]
    } else {
      character(0)
    }
  }, error = function(e) character(0))
  
  # Director patterns
  if("Director" %in% names(movies)) {
    valid_directors <- movies$Director[!is.na(movies$Director) & movies$Director != ""]
    if(length(valid_directors) > 0) {
      patterns$directors <- names(sort(table(valid_directors), decreasing = TRUE))[1:min(10, length(unique(valid_directors)))]
    } else {
      patterns$directors <- c("Unknown Director")
    }
  } else {
    patterns$directors <- c("Unknown Director")
  }
  
  return(patterns)
}

safe_str_extract <- function(string, pattern) {
  if(is.null(string) || all(is.na(string)) || length(string) == 0) {
    return(character(0))
  }
  
  # Remove NA strings
  string <- string[!is.na(string) & string != ""]
  
  if(length(string) == 0) {
    return(character(0))
  }
  
  result <- tryCatch({
    extracted <- str_extract_all(string, pattern)
    unlist(extracted)
  }, error = function(e) character(0))
  
  # Remove NAs from result
  result <- result[!is.na(result) & result != ""]
  
  return(result %||% character(0))
}

# TITLE GENERATION

generate_title_with_ai <- function(movies, model, originality) {
  titles <- model$patterns$titles
  title_freq <- model$patterns$title_freq
  
  if(length(titles) == 0) {
    return("The Untitled Story")
  }
  
  title <- switch(model$type,
    "transformer" = generate_transformer_title(titles, title_freq, model$temperature, originality),
    "lstm" = generate_lstm_title(titles, title_freq, model$temperature, originality),
    "mcmc" = generate_mcmc_title(titles, title_freq, model$temperature, originality),
    generate_ensemble_title(titles, title_freq, originality)
  )
  
  return(clean_generated_text(title))
}

generate_transformer_title <- function(titles, word_freq, temperature, originality) {
  bigrams <- list()
  
  for(title in titles) {
    words <- strsplit(title, "\\s+")[[1]]
    if(length(words) >= 2) {
      for(i in 1:(length(words)-1)) {
        key <- words[i]
        if(!key %in% names(bigrams)) bigrams[[key]] <- list()
        bigrams[[key]][[words[i+1]]] <- (bigrams[[key]][[words[i+1]]] %||% 0) + 1
      }
    }
  }
  
  start_words <- intersect(c("The", "A", "Dark", "Last", "Final"), names(word_freq))
  if(length(start_words) == 0) start_words <- names(word_freq)[1:min(5, length(word_freq))]
  
  current_word <- safe_sample(start_words, 1)
  title_words <- c(current_word)
  
  for(i in 2:sample(2:4, 1)) {
    if(current_word %in% names(bigrams) && length(bigrams[[current_word]]) > 0) {
      next_probs <- unlist(bigrams[[current_word]])
      
      if(temperature != 1.0) {
        next_probs <- next_probs^(1/temperature)
      }
      
      if(length(next_probs) > 0) {
        next_probs <- next_probs / sum(next_probs)
        current_word <- safe_sample(names(next_probs), 1, prob = next_probs)
        if(!is.null(current_word)) {
          title_words <- c(title_words, current_word)
        } else {
          break
        }
      } else {
        break
      }
    } else {
      break
    }
  }
  
  return(paste(title_words, collapse = " "))
}

generate_lstm_title <- function(titles, word_freq, temperature, originality) {
  # Ensure we have valid input
  if(length(titles) == 0 || length(word_freq) == 0) {
    return("The Story")
  }
  
  sequence_length <- sample(2:4, 1)
  title_words <- character(sequence_length)
  
  # Get available words and remove NAs
  available_words <- names(word_freq)
  available_words <- available_words[!is.na(available_words)]
  available_words <- available_words[1:min(10, length(available_words))]
  
  if(length(available_words) == 0) {
    return("The Story")
  }
  
  # Initialize first word
  title_words[1] <- safe_sample(available_words, 1)
  
  if(is.null(title_words[1])) {
    title_words[1] <- "The"
  }
  
  for(i in 2:sequence_length) {
    # Get context words (remove NAs)
    context_start <- max(1, i-2)
    context_end <- i-1
    context <- title_words[context_start:context_end]
    context <- context[!is.na(context) & context != ""]
    
    similar_words <- character()
    
    # Find similar contexts in training data
    for(title in titles) {
      if(is.na(title) || title == "") next
      
      words <- strsplit(title, "\\s+")[[1]]
      words <- words[!is.na(words) & words != ""]
      
      if(length(words) < 2) next
      
      for(j in 1:(length(words)-1)) {
        if(j <= length(words) && !is.na(words[j]) && words[j] %in% context) {
          if((j+1) <= length(words) && !is.na(words[j+1])) {
            similar_words <- c(similar_words, words[j+1])
          }
        }
      }
    }
    
    # Remove NAs and empty strings
    similar_words <- similar_words[!is.na(similar_words) & similar_words != ""]
    
    if(length(similar_words) > 0) {
      title_words[i] <- safe_sample(similar_words, 1)
    } else {
      # Fallback to frequency-based selection
      fallback_words <- names(word_freq)
      fallback_words <- fallback_words[!is.na(fallback_words)]
      fallback_words <- fallback_words[1:min(20, length(fallback_words))]
      
      if(length(fallback_words) > 0) {
        title_words[i] <- safe_sample(fallback_words, 1)
      } else {
        title_words[i] <- "Story"
      }
    }
    
    # Final safety check
    if(is.null(title_words[i]) || is.na(title_words[i])) {
      title_words[i] <- "Story"
    }
  }
  
  # Clean up and return
  title_words <- title_words[!is.na(title_words) & title_words != ""]
  
  if(length(title_words) == 0) {
    return("The Story")
  }
  
  return(paste(title_words, collapse = " "))
}

generate_mcmc_title <- function(titles, word_freq, temperature, originality) {
  current_title <- safe_sample(titles, 1)
  best_title <- current_title
  best_score <- score_title(current_title, titles, originality)
  
  for(iter in 1:100) {
    words <- strsplit(current_title, "\\s+")[[1]]
    
    if(runif(1) < 0.5 && length(words) > 1) {
      idx <- sample(1:length(words), 1)
      available_words <- names(word_freq)[1:min(30, length(word_freq))]
      words[idx] <- safe_sample(available_words, 1)
    } else if(length(words) < 5) {
      available_words <- names(word_freq)[1:min(30, length(word_freq))]
      new_word <- safe_sample(available_words, 1)
      words <- append(words, new_word, after = sample(0:length(words), 1))
    }
    
    proposed_title <- paste(words, collapse = " ")
    proposed_score <- score_title(proposed_title, titles, originality)
    
    if(proposed_score > best_score || 
       runif(1) < exp((proposed_score - best_score) / temperature)) {
      current_title <- proposed_title
      if(proposed_score > best_score) {
        best_title <- proposed_title
        best_score <- proposed_score
      }
    }
  }
  
  return(best_title)
}

generate_ensemble_title <- function(titles, word_freq, originality) {
  if(originality < 5) {
    base <- safe_sample(titles[1:min(10, length(titles))], 1)
    words <- strsplit(base, "\\s+")[[1]]
    if(length(words) > 1) {
      available_words <- names(word_freq)[5:min(20, length(word_freq))]
      words[sample(2:length(words), 1)] <- safe_sample(available_words, 1)
    }
    return(paste(words, collapse = " "))
  } else {
    num_words <- sample(2:4, 1)
    available_words <- names(word_freq)[1:min(30, length(word_freq))]
    selected_words <- safe_sample(available_words, num_words)
    return(paste(selected_words, collapse = " "))
  }
}

score_title <- function(title, reference_titles, originality) {
  score <- 0
  
  words <- strsplit(title, "\\s+")[[1]]
  if(length(words) >= 2 && length(words) <= 4) score <- score + 1
  
  if(!(title %in% reference_titles)) score <- score + originality/10
  
  if(length(words) >= 2) {
    for(i in 1:(length(words)-1)) {
      bigram <- paste(words[i], words[i+1])
      if(any(grepl(bigram, reference_titles))) score <- score + 0.5
    }
  }
  
  return(score)
}

# PLOT GENERATION

generate_plot_with_ai <- function(movies, model, genre, title) {
  plots <- movies$Plot[!is.na(movies$Plot) & nchar(movies$Plot) > 50]
  
  if(length(plots) < 5) {
    return(paste("In this", tolower(genre), "adventure,", title, 
                 "explores themes of courage and determination."))
  }
  
  elements <- extract_plot_elements(plots)
  
  plot <- switch(model$type,
    "transformer" = generate_transformer_plot(elements, model$temperature),
    "lstm" = generate_lstm_plot(elements, model$temperature),
    generate_ensemble_plot(elements)
  )
  
  return(clean_generated_text(plot))
}

extract_plot_elements <- function(plots) {
  elements <- list()
  
  # Remove NA plots
  plots <- plots[!is.na(plots) & plots != ""]
  
  if(length(plots) == 0) {
    return(list(
      openings = c("In a world of endless possibilities"),
      conflicts = c("faces an impossible challenge"),
      resolutions = c("A journey that will change everything."),
      characters = c("brave hero")
    ))
  }
  
  # Extract openings
  elements$openings <- unique(substr(plots, 1, 100))
  elements$openings <- elements$openings[!is.na(elements$openings) & elements$openings != ""]
  elements$openings <- elements$openings[1:min(10, length(elements$openings))]
  
  # Extract conflicts using safe_str_extract
  elements$conflicts <- safe_str_extract(plots, "(must|has to|needs to|discovers) [^.]+")
  if(length(elements$conflicts) > 0) {
    elements$conflicts <- unique(elements$conflicts)[1:min(10, length(elements$conflicts))]
  }
  
  # Extract resolutions using safe_str_extract
  elements$resolutions <- safe_str_extract(plots, "[A-Z][^.]+\\.$")
  if(length(elements$resolutions) > 0) {
    elements$resolutions <- unique(elements$resolutions)[1:min(10, length(elements$resolutions))]
  }
  
  # Extract characters using safe_str_extract
  elements$characters <- safe_str_extract(plots, "(young|old|brilliant|mysterious|unlikely) [a-z]+")
  if(length(elements$characters) > 0) {
    elements$characters <- unique(elements$characters)[1:min(10, length(elements$characters))]
  }
  
  # Ensure all elements have at least one item
  if(length(elements$openings) == 0) elements$openings <- c("In a world of endless possibilities")
  if(length(elements$conflicts) == 0) elements$conflicts <- c("faces an impossible challenge")
  if(length(elements$resolutions) == 0) elements$resolutions <- c("A journey that will change everything.")
  if(length(elements$characters) == 0) elements$characters <- c("brave hero")
  
  return(elements)
}

generate_transformer_plot <- function(elements, temperature) {
  opening <- safe_sample(elements$openings, 1) %||% "In a world where anything is possible,"
  conflict <- safe_sample(elements$conflicts, 1) %||% "our hero faces an impossible challenge"
  
  if(temperature > 1.0 && length(elements$characters) > 0) {
    character <- safe_sample(elements$characters, 1)
    if(!is.null(character)) {
      conflict <- paste("The", character, conflict)
    }
  }
  
  resolution <- safe_sample(elements$resolutions, 1) %||% "A journey that will change everything."
  
  plot <- paste(opening, conflict, ".", resolution)
  plot <- gsub("\\s+", " ", plot)
  plot <- gsub("\\.\\.+", ".", plot)
  
  return(plot)
}

generate_lstm_plot <- function(elements, temperature) {
  plot_parts <- character(3)
  
  # Part 1: Opening
  if(!is.null(elements$openings) && length(elements$openings) > 0) {
    valid_openings <- elements$openings[!is.na(elements$openings) & elements$openings != ""]
    if(length(valid_openings) > 0) {
      plot_parts[1] <- safe_sample(valid_openings, 1)
    }
  }
  
  if(is.null(plot_parts[1]) || is.na(plot_parts[1]) || plot_parts[1] == "") {
    plot_parts[1] <- "In a world of endless possibilities,"
  }
  
  # Part 2: Conflict
  if(!is.null(elements$conflicts) && length(elements$conflicts) > 0) {
    valid_conflicts <- elements$conflicts[!is.na(elements$conflicts) & elements$conflicts != ""]
    if(length(valid_conflicts) > 0) {
      conflict <- safe_sample(valid_conflicts, 1)
      if(!is.null(conflict) && !is.na(conflict)) {
        plot_parts[2] <- paste("our protagonist", conflict)
      }
    }
  }
  
  if(is.null(plot_parts[2]) || is.na(plot_parts[2]) || plot_parts[2] == "") {
    plot_parts[2] <- "our hero faces unprecedented challenges"
  }
  
  # Part 3: Resolution
  if(!is.null(elements$resolutions) && length(elements$resolutions) > 0) {
    valid_resolutions <- elements$resolutions[!is.na(elements$resolutions) & elements$resolutions != ""]
    if(length(valid_resolutions) > 0) {
      plot_parts[3] <- safe_sample(valid_resolutions, 1)
    }
  }
  
  if(is.null(plot_parts[3]) || is.na(plot_parts[3]) || plot_parts[3] == "") {
    plot_parts[3] <- "A journey that will change everything."
  }
  
  # Final safety check
  plot_parts <- plot_parts[!is.na(plot_parts) & plot_parts != ""]
  
  if(length(plot_parts) == 0) {
    return("An extraordinary adventure unfolds.")
  }
  
  return(paste(plot_parts, collapse = " "))
}


generate_ensemble_plot <- function(elements) {
  opening <- safe_sample(elements$openings, 1) %||% "An extraordinary story begins"
  conflict <- safe_sample(elements$conflicts, 1) %||% "when fate intervenes"
  resolution <- safe_sample(elements$resolutions, 1) %||% "leading to an unforgettable conclusion."
  
  plot <- paste(opening, conflict, resolution)
  plot <- gsub("\\s+", " ", plot)
  plot <- gsub("([.!?])\\1+", "\\1", plot)
  
  return(plot)
}

# TEAM SELECTION

select_team_with_ml <- function(movies, optimization) {
  team <- list(director = "Acclaimed Director", cast = "Star Ensemble")
  
  if("Director" %in% names(movies)) {
    director_stats <- movies %>%
      filter(!is.na(Director)) %>%
      group_by(Director) %>%
      summarise(
        count = n(),
        avg_revenue = mean(BoxOffice_num, na.rm = TRUE),
        avg_rating = mean(imdbRating, na.rm = TRUE),
        .groups = 'drop'
      ) %>%
      filter(count >= 1)
    
    if(nrow(director_stats) > 0) {
      if(optimization == "boxoffice") {
        team$director <- director_stats %>%
          arrange(desc(avg_revenue)) %>%
          slice(1) %>%
          pull(Director)
      } else if(optimization == "rating") {
        team$director <- director_stats %>%
          arrange(desc(avg_rating)) %>%
          slice(1) %>%
          pull(Director)
      } else {
        team$director <- director_stats %>%
          mutate(score = scale(avg_revenue)[,1] + scale(avg_rating)[,1]) %>%
          arrange(desc(score)) %>%
          slice(1) %>%
          pull(Director)
      }
    }
  }
  
  if("Actors" %in% names(movies)) {
    all_actors <- movies$Actors %>%
      na.omit() %>%
      str_split(", ") %>%
      unlist()
    
    if(length(all_actors) >= 3) {
      actor_freq <- sort(table(all_actors), decreasing = TRUE)
      top_actors <- names(actor_freq)[1:min(3, length(actor_freq))]
      team$cast <- paste(top_actors, collapse = ", ")
    }
  }
  
  return(team)
}

# CONFIGURATION OPTIMIZATION 

optimize_movie_config <- function(movies, target_boxoffice, optimization) {
  config <- list()
  
  successful_movies <- movies %>%
    filter(!is.na(BoxOffice_num), !is.na(imdbRating))
  
  if(nrow(successful_movies) > 0) {
    config$runtime <- round(median(successful_movies$Runtime_num, na.rm = TRUE))
    
    genre_performance <- successful_movies %>%
      group_by(Genre) %>%
      summarise(
        count = n(),
        avg_revenue = mean(BoxOffice_num, na.rm = TRUE),
        avg_rating = mean(imdbRating, na.rm = TRUE),
        .groups = 'drop'
      ) %>%
      filter(count >= 2)
    
    if(nrow(genre_performance) > 0) {
      if(optimization == "boxoffice") {
        config$genres <- genre_performance %>%
          arrange(desc(avg_revenue)) %>%
          slice(1) %>%
          pull(Genre)
      } else {
        config$genres <- genre_performance %>%
          arrange(desc(avg_rating)) %>%
          slice(1) %>%
          pull(Genre)
      }
    } else {
      config$genres <- successful_movies$Genre[1]
    }
    
    if("Released" %in% names(successful_movies)) {
      release_months <- month(successful_movies$Released, label = FALSE)
      release_months <- release_months[!is.na(release_months)]
      if(length(release_months) > 0) {
        config$release_month <- as.numeric(names(sort(table(release_months), decreasing = TRUE)[1]))
      } else {
        config$release_month <- 6
      }
    } else {
      config$release_month <- 6
    }
    
    if("Rated" %in% names(successful_movies)) {
      rating_performance <- successful_movies %>%
        filter(Rated %in% c("PG", "PG-13", "R")) %>%
        group_by(Rated) %>%
        summarise(
          avg_revenue = mean(BoxOffice_num, na.rm = TRUE),
          .groups = 'drop'
        )
      
      if(nrow(rating_performance) > 0) {
        config$mpaa_rating <- rating_performance %>%
          arrange(desc(avg_revenue)) %>%
          slice(1) %>%
          pull(Rated)
      } else {
        config$mpaa_rating <- "PG-13"
      }
    } else {
      config$mpaa_rating <- "PG-13"
    }
    
  } else {
    config$runtime <- 120
    config$genres <- "Drama, Thriller"
    config$release_month <- 6
    config$mpaa_rating <- "PG-13"
  }
  
  return(config)
}

# PERFORMANCE PREDICTION 

predict_performance_ml <- function(movie, reference_movies, optimization) {
  performance <- list()
  
  similar_movies <- reference_movies %>%
    filter(
      grepl(strsplit(movie$genres, ",")[[1]][1], Genre),
      abs(Runtime_num - movie$runtime) < 30
    )
  
  if(nrow(similar_movies) > 0) {
    performance$revenue <- mean(similar_movies$BoxOffice_num, na.rm = TRUE) / 1e6
    performance$rating <- mean(similar_movies$imdbRating, na.rm = TRUE)
    
    if(optimization == "boxoffice") {
      performance$revenue <- performance$revenue * 1.2
    } else if(optimization == "rating") {
      performance$rating <- min(9.0, performance$rating + 0.5)
    }
    
    performance$confidence <- min(0.9, 0.5 + nrow(similar_movies) * 0.05)
    
  } else {
    performance$revenue <- 150
    performance$rating <- 7.0
    performance$confidence <- 0.5
  }
  
  performance$breakdown <- list(
    similar_movies_count = nrow(similar_movies),
    genre_match = TRUE,
    runtime_match = TRUE,
    optimization_applied = optimization
  )
  
  return(performance)
}

# RESULT UI

create_enhanced_result_ui <- function(movie, performance, model_info) {
  tags$div(
    style = "background: white; padding: 25px; border-radius: 12px; 
            box-shadow: 0 4px 12px rgba(0,0,0,0.1); margin-top: 20px;",
    
    tags$div(
      style = "background: linear-gradient(135deg, #667eea 0%, #764ba2 100%); 
              color: white; padding: 15px; border-radius: 8px; margin-bottom: 20px;",
      tags$div(
        style = "display: flex; justify-content: space-between; align-items: center;",
        tags$h4(movie$title, style = "margin: 0;"),
        tags$small(
          "Generated with ", 
          toupper(model_info$type), 
          " model",
          style = "opacity: 0.9;"
        )
      )
    ),
    
    tags$div(
      style = "display: grid; grid-template-columns: repeat(3, 1fr); gap: 15px; margin-bottom: 25px;",
      
      tags$div(
        style = "text-align: center; padding: 15px; background: #f7fafc; border-radius: 8px;",
        tags$div(style = "font-size: 24px; font-weight: bold; color: #2d3748;",
                paste0("$", round(performance$revenue), "M")),
        tags$small("Predicted Box Office", style = "color: #718096;")
      ),
      
      tags$div(
        style = "text-align: center; padding: 15px; background: #f7fafc; border-radius: 8px;",
        tags$div(style = "font-size: 24px; font-weight: bold; color: #2d3748;",
                round(performance$rating, 1)),
        tags$small("IMDb Rating", style = "color: #718096;")
      ),
      
      tags$div(
        style = "text-align: center; padding: 15px; background: #f7fafc; border-radius: 8px;",
        tags$div(style = "font-size: 24px; font-weight: bold; color: #2d3748;"),
        tags$div(style = "font-size: 24px; font-weight: bold; color: #2d3748;",
                paste0(round(performance$confidence * 100), "%")),
        tags$small("Prediction Confidence", style = "color: #718096;")
      )
    ),
    
    tags$div(
      style = "background: #edf2f7; padding: 20px; border-radius: 8px; margin-bottom: 20px;",
      tags$h5("📝 AI-Generated Plot", style = "margin-bottom: 15px;"),
      tags$p(movie$plot, style = "line-height: 1.8; color: #4a5568; margin: 0;")
    ),
    
    tags$div(
      style = "background: #e6fffa; padding: 20px; border-radius: 8px; margin-bottom: 20px;",
      tags$h5("🎬 Production Configuration", style = "margin-bottom: 15px;"),
      
      tags$div(
        style = "display: grid; grid-template-columns: 1fr 1fr; gap: 20px;",
        
        tags$div(
          tags$p(tags$strong("Director: "), movie$director),
          tags$p(tags$strong("Cast: "), movie$cast),
          tags$p(tags$strong("Runtime: "), paste(movie$runtime, "minutes"))
        ),
        
        tags$div(
          tags$p(tags$strong("Genres: "), movie$genres),
          tags$p(tags$strong("MPAA Rating: "), movie$mpaa_rating),
          tags$p(tags$strong("Release Month: "), month.name[movie$release_month])
        )
      )
    ),
    
    tags$div(
      style = "background: #f0f4f8; padding: 20px; border-radius: 8px;",
      tags$h5("🤖 AI Generation Details", style = "margin-bottom: 15px;"),
      
      tags$div(
        style = "font-size: 14px; color: #4a5568;",
        tags$p(
          tags$strong("Model: "), toupper(movie$ai_model), br(),
          tags$strong("Optimization: "), 
          switch(movie$optimization,
            "boxoffice" = "Maximizing box office revenue",
            "rating" = "Maximizing critical acclaim",
            "Balanced approach"
          ), br(),
          tags$strong("Based on: "), 
          performance$breakdown$similar_movies_count, 
          " similar successful movies"
        )
      )
    )
  )
}

# VALIDATION FUNCTIONS

validate_movie <- function(movie) {
  required_fields <- c("title", "plot", "director", "cast", "genres", 
                      "runtime", "release_month", "mpaa_rating")
  
  for(field in required_fields) {
    if(is.null(movie[[field]])) {
      movie[[field]] <- switch(field,
        "title" = "Untitled Project",
        "plot" = "A compelling story awaits.",
        "director" = "Visionary Director",
        "cast" = "Talented Ensemble",
        "genres" = "Drama",
        "runtime" = 120,
        "release_month" = 6,
        "mpaa_rating" = "PG-13"
      )
    }
  }
  
  return(movie)
}

validate_performance <- function(performance) {
  performance$revenue <- performance$revenue %||% 150
  performance$rating <- performance$rating %||% 7.0
  performance$confidence <- performance$confidence %||% 0.7
  
  performance$revenue <- max(10, min(1000, performance$revenue))
  performance$rating <- max(1, min(10, performance$rating))
  performance$confidence <- max(0, min(1, performance$confidence))
  
  return(performance)
}

# ERROR RECOVERY

recover_from_error <- function(error_message, input) {
  cat("Error in AI generation:", error_message, "\n")
  
  fallback_movie <- list(
    title = "The Journey",
    plot = "An inspiring tale of courage and determination unfolds.",
    director = "Acclaimed Director",
    cast = "Star-studded Cast",
    genres = "Drama, Adventure",
    runtime = 120,
    release_month = 6,
    mpaa_rating = "PG-13",
    ai_model = input$ai_model_type %||% "ensemble",
    optimization = input$optimization_type %||% "balanced"
  )
  
  fallback_performance <- list(
    revenue = 150,
    rating = 7.0,
    confidence = 0.5,
    breakdown = list(
      similar_movies_count = 0,
      genre_match = FALSE,
      runtime_match = FALSE,
      optimization_applied = "none"
    )
  )
  
  return(list(
    movie = fallback_movie,
    performance = fallback_performance,
    error = error_message
  ))
}

# DATA VALIDATION

validate_input_data <- function(movies_data) {
  if(is.null(movies_data) || !is.data.frame(movies_data)) {
    stop("Invalid movie data format")
  }
  
  if(nrow(movies_data) == 0) {
    stop("No movies in dataset")
  }
  
  required_cols <- c("Title", "Plot", "Genre")
  missing_cols <- setdiff(required_cols, names(movies_data))
  
  if(length(missing_cols) > 0) {
    stop(paste("Missing required columns:", paste(missing_cols, collapse = ", ")))
  }
  
  valid_rows <- movies_data %>%
    filter(!is.na(Title), !is.na(Plot), nchar(Plot) > 10)
  
  if(nrow(valid_rows) < 10) {
    warning("Limited valid data available")
  }
  
  return(TRUE)
}

# CACHE MANAGEMENT

create_pattern_cache <- function() {
  cache <- new.env(parent = emptyenv())
  
  cache$get <- function(key) {
    if(exists(key, envir = cache)) {
      return(get(key, envir = cache))
    }
    return(NULL)
  }
  
  cache$set <- function(key, value) {
    assign(key, value, envir = cache)
  }
  
  cache$clear <- function() {
    rm(list = ls(envir = cache), envir = cache)
  }
  
  return(cache)
}

pattern_cache <- create_pattern_cache()

extract_patterns_cached <- function(movies, cache_key) {
  cached_patterns <- pattern_cache$get(cache_key)
  if(!is.null(cached_patterns)) {
    return(cached_patterns)
  }
  
  patterns <- extract_patterns_optimized(movies)
  pattern_cache$set(cache_key, patterns)
  
  return(patterns)
}

# SAFE WRAPPER

safe_ai_generation <- function(input, movies_clean) {
  result <- tryCatch({
    validate_input_data(movies_clean)
    return(list(success = TRUE))
  }, error = function(e) {
    recovery <- recover_from_error(e$message, input)
    return(list(
      success = FALSE,
      movie = recovery$movie,
      performance = recovery$performance,
      error = e$message
    ))
  })
  
  return(result)
}

# DEBUG HELPER

debug_generation <- function(step, data) {
  if(getOption("ai_movie_debug", FALSE)) {
    cat("\n=== Debug:", step, "===\n")
    print(str(data))
    cat("==================\n")
  }
}
```

# Test Performance {data-icon="fa-chart-area"}

## Column {data-width=70%}

### Figure 1: MSE and R² Comparison

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)

# Helper to compute metrics
get_metrics <- function(y, yhat) {
  mse <- mean((y - yhat)^2)
  r2  <- 1 - sum((y - yhat)^2) / sum((y - mean(y))^2)
  c(MSE = mse, R2 = r2)
}

# Train models and get train/test split
models_static <- build_ensemble_model(movies_clean)

test_data  <- models_static$test_data
y_test_log <- log(test_data$BoxOffice_num)

# Predictions on test set (log scale)

## GAM & Linear Model: use full test_data
pred_gam_log <- predict(models_static$gam, newdata = test_data)
pred_lm_log  <- predict(models_static$lm,  newdata = test_data)

## RF & SVM: numeric features (like training)
rf_test_features <- test_data %>%
  dplyr::select_if(is.numeric) %>%
  dplyr::select(-BoxOffice_num)

idx_complete <- complete.cases(rf_test_features)
rf_test_features <- rf_test_features[idx_complete, ]
y_test_log_rf    <- y_test_log[idx_complete]

pred_rf_log  <- predict(models_static$rf,  newdata = rf_test_features)
pred_svm_log <- predict(models_static$svm, newdata = rf_test_features)

# Compute metrics for each model
m_gam <- get_metrics(y_test_log,    pred_gam_log)
m_lm  <- get_metrics(y_test_log,    pred_lm_log)
m_rf  <- get_metrics(y_test_log_rf, pred_rf_log)
m_svm <- get_metrics(y_test_log_rf, pred_svm_log)

metrics_df <- tibble(
  Model = factor(c("GAM", "Random Forest", "Linear Model", "SVM"),
                 levels = c("GAM", "Random Forest", "Linear Model", "SVM")),
  MSE = c(m_gam["MSE"], m_rf["MSE"], m_lm["MSE"], m_svm["MSE"]),
  R2  = c(m_gam["R2"],  m_rf["R2"],  m_lm["R2"],  m_svm["R2"])
)

# Long format for faceted bar plot
metrics_long <- metrics_df %>%
  pivot_longer(cols = c(MSE, R2),
               names_to = "Metric",
               values_to = "Value")

ggplot(metrics_long, aes(x = Model, y = Value, fill = Model)) +
  geom_col() +
  facet_wrap(~ Metric, scales = "free_y") +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)  # <-- Fix overlap
  ) +
  labs(
    title = "Model Performance (MSE and R²)",
    x = "Model",
    y = "Value"
  )

```

## Column {data-width=70%}

### Figure 2: Residual Density Comparison
```{r}
library(dplyr)
library(ggplot2)
library(tibble)

# Fit models and get train/test split
models_static <- build_ensemble_model(movies_clean)

test_data  <- models_static$test_data
y_test_log <- log(test_data$BoxOffice_num)

# Predictions (on log scale)

## GAM & Linear Model: use full test_data
pred_gam_log <- predict(models_static$gam, newdata = test_data)
pred_lm_log  <- predict(models_static$lm,  newdata = test_data)

## RF & SVM: numeric features as in training
rf_test_features <- test_data %>%
  dplyr::select_if(is.numeric) %>%
  dplyr::select(-BoxOffice_num)

idx_complete      <- complete.cases(rf_test_features)
rf_test_features  <- rf_test_features[idx_complete, ]
y_test_log_rf     <- y_test_log[idx_complete]

pred_rf_log  <- predict(models_static$rf,  newdata = rf_test_features)
pred_svm_log <- predict(models_static$svm, newdata = rf_test_features)

# Residuals = actual - predicted (log scale)
resid_df <- bind_rows(
  tibble(Model = "GAM",
         residual = y_test_log - pred_gam_log),
  tibble(Model = "Linear Model",
         residual = y_test_log - pred_lm_log),
  tibble(Model = "Random Forest",
         residual = y_test_log_rf - pred_rf_log),
  tibble(Model = "SVM",
         residual = y_test_log_rf - pred_svm_log)
)

# Density plot of residuals
ggplot(resid_df, aes(x = residual, fill = Model, colour = Model)) +
  geom_density(alpha = 0.25) +
  theme_minimal() +
  labs(
    title = "Residual Density Comparison Across Models",
    x = "Residual (log Box Office)",
    y = "Density"
  )
```

## Column {data-width=30%}

### 📘 How to Read These Graphs
What this figure shows:

Left panel (MSE): Mean Squared Error

- Measures the average squared distance between predicted and true log box office.

- Lower bars are better → the model’s predictions stay closer to the actual values.

Right panel (R²): R-squared

- Measures the fraction of variability in log box office that the model explains.

- Higher bars are better → the model captures more of the real signal in the data.

How to interpret the current bars

Random Forest has the lowest MSE and highest R², so it is the best overall performer.

SVM also performs well, with reasonably low MSE and high R², but not as strong as Random Forest.

GAM and the Linear Model have larger MSE and lower R², meaning they miss more structure in the data and make less accurate predictions.

Understanding Figure 2: Residual Density Comparison

What this figure shows:

- Each curve is the distribution of residuals (actual − predicted log box office) for one model.

- The x-axis is the residual value; the y-axis is density (how often that residual size occurs).

A good model will have:

- Residuals clustered tightly around 0 (narrow, tall peak at 0),

- And relatively few large positive or negative residuals (thin tails).

How to interpret the current curves?

Random Forest and SVM have sharper peaks near zero and thinner tails, indicating smaller, more consistent errors.

GAM and the Linear Model show wider, flatter curves, meaning their residuals are more spread out, with more frequent large errors.

If you see systematic skew (more mass on one side), that suggests the model tends to over- or under-predict for certain movies.

# About {data-icon="fa-info-circle"}

## Column

### 🎬 About Investment Time Machine

```{r}
tags$div(
  style = "max-width: 900px; margin: 0 auto; padding: 20px;",
  
  # Header
  tags$div(
    style = "background: linear-gradient(135deg, #1a1f3a 0%, #2d3561 100%); 
            padding: 40px; border-radius: 16px; color: white; margin-bottom: 30px;
            box-shadow: 0 10px 30px rgba(0,0,0,0.2); text-align: center;",
    
    tags$h1("Movie Investment Time Machine", 
            style = "margin: 0 0 15px 0; font-size: 42px; font-weight: 700;"),
    tags$h3("Data-Driven Insights for Film Investment", 
            style = "opacity: 0.9; font-weight: 300; margin: 0 0 25px 0;"),
    
    tags$p(
      style = "font-size: 18px; line-height: 1.8; max-width: 700px; margin: 0 auto;",
      "Make informed investment decisions by understanding how movies perform across different time periods. ",
      "Our machine learning models predict box office revenue, helping investors evaluate potential returns",
      "and optimize release timing strategies."
    )
  ),
  
  # Features Grid
  tags$div(
    style = "display: grid; grid-template-columns: repeat(auto-fit, minmax(250px, 1fr)); 
            gap: 20px; margin-bottom: 30px;",
    
    # Feature 1
    tags$div(
      style = "background: white; padding: 25px; border-radius: 12px; 
              box-shadow: 0 4px 12px rgba(0,0,0,0.08); text-align: center;",
      tags$div(style = "font-size: 36px; margin-bottom: 10px;", "📊"),
      tags$h4("Time Travel Analysis", style = "color: #1e293b; margin: 0 0 10px 0;"),
      tags$p(style = "color: #64748b; margin: 0; font-size: 14px;",
             "Predict box office performance across 25 years (2000-2025)")
    ),
    
    # Feature 2
    tags$div(
      style = "background: white; padding: 25px; border-radius: 12px; 
              box-shadow: 0 4px 12px rgba(0,0,0,0.08); text-align: center;",
      tags$div(style = "font-size: 36px; margin-bottom: 10px;", "🎯"),
      tags$h4("What-If Scenarios", style = "color: #1e293b; margin: 0 0 10px 0;"),
      tags$p(style = "color: #64748b; margin: 0; font-size: 14px;",
             "Test how parameter changes affect potential returns")
    ),
    
    # Feature 3
    tags$div(
      style = "background: white; padding: 25px; border-radius: 12px; 
              box-shadow: 0 4px 12px rgba(0,0,0,0.08); text-align: center;",
      tags$div(style = "font-size: 36px; margin-bottom: 10px;", "🤖"),
      tags$h4("AI Movie Generator", style = "color: #1e293b; margin: 0 0 10px 0;"),
      tags$p(style = "color: #64748b; margin: 0; font-size: 14px;",
             "Generate optimized movie concepts for target revenue")
    )
  ),
  
  # How it Works
  tags$div(
    style = "background: #f8fafc; padding: 30px; border-radius: 12px; margin-bottom: 30px;",
    
    tags$h3("How It Works", style = "color: #1e293b; margin: 0 0 20px 0; text-align: center;"),
    
    tags$div(
      style = "display: grid; grid-template-columns: repeat(auto-fit, minmax(200px, 1fr)); 
              gap: 30px; text-align: center;",
      
      tags$div(
        tags$div(
          style = "background: #059669; color: white; width: 40px; height: 40px; 
                  border-radius: 50%; display: flex; align-items: center; 
                  justify-content: center; margin: 0 auto 10px; font-weight: bold;",
          "1"
        ),
        tags$strong("Select Movie", style = "color: #1e293b;"), br(),
        tags$small("Choose from our database", style = "color: #64748b;")
      ),
      
      tags$div(
        tags$div(
          style = "background: #059669; color: white; width: 40px; height: 40px; 
                  border-radius: 50%; display: flex; align-items: center; 
                  justify-content: center; margin: 0 auto 10px; font-weight: bold;",
          "2"
        ),
        tags$strong("Run Analysis", style = "color: #1e293b;"), br(),
        tags$small("ML models predict performance", style = "color: #64748b;")
      ),
      
      tags$div(
        tags$div(
          style = "background: #059669; color: white; width: 40px; height: 40px; 
                  border-radius: 50%; display: flex; align-items: center; 
                  justify-content: center; margin: 0 auto 10px; font-weight: bold;",
          "3"
        ),
        tags$strong("Get Insights", style = "color: #1e293b;"), br(),
        tags$small("View predictions & recommendations", style = "color: #64748b;")
      )
    )
  ),
  
  # Tech Stack & Credits
  tags$div(
    style = "background: white; padding: 30px; border-radius: 12px; 
            box-shadow: 0 4px 12px rgba(0,0,0,0.08); text-align: center;",
    
    tags$h4("Built With", style = "color: #1e293b; margin: 0 0 15px 0;"),
    
    tags$p(
      style = "color: #64748b; margin: 0 0 20px 0;",
      "R • Shiny • Plotly • tidyverse • randomForest • mgcv • flexdashboard"
    ),
    
    tags$hr(style = "margin: 20px auto; width: 100px; border-color: #e5e7eb;"),
    
    tags$p(
      style = "color: #1e293b; margin: 0;",
      tags$strong("Created by Purrgramming Team"), br(),
      tags$small(
        style = "color: #64748b;",
        "Statistical Programming Paradigms and Workflows • 2025"
      )
    )
  )
)
```